---
title: 'Example File: Satellite Data'
author: "Alexis Denhard"
date: "April 13, 2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

rm(list = ls()) #clear environment

#load in necessary libraries
library(astsa)
library(imputeTS)
library(forecast)
library(fields)
library(lubridate) #yday function
library(iemisc) #cosd function
library(purrr) #detect_index function
```

For this example file, we will use the TBL (NSRDB) data.

``` {r}
#load in csv file for TBL (NSRDB) data
csdat2017 = suppressWarnings(read.csv("D:/Work/2017_data/TBL/TBL_40.09-105.18.csv"
                                      , header = TRUE)) 

#Remove first four NA rowws
csdat2017 = csdat2017[-1,]
csdat2017 = csdat2017[-1,]
csdat2017 = csdat2017[-1,]
csdat2017 = csdat2017[-1,]

#We will calculate clearness index as follows:

df = as.Date(csdat2017$time_index) #change to date variable
doy = yday(df) #doy - day of year
B = 2*pi*doy/365
Rfact2 = 1.00011 + 0.034221 * cos(B)+ 0.00128*sin(B)+ 0.000719*cos(2*B)+0.000077*sin(2*B)
ETRN = 1361*Rfact2 #extraterrestrial irradiance
SZA = csdat2017$solar_zenith_angle #solar zenith angle

csdat2017 = within(csdat2017, ghi[fill_flag != 0] <- NA) #set values to null for fill flag criteria where not equal to zero
ghi = csdat2017$ghi #global horizontal irradiance
Kt = ghi / (ETRN * cosd(SZA)) #clearness index

Kt.observed = as.ts(Kt) #set a variable for observed observations since we will synthetically remove points from Kt variable
index = which(is.na(Kt.observed)) #set a variable for indices of null values

#Visualize first 1000 observations of Kt
plot.ts(Kt.observed[1:1000], ylab = "Kt Observed")
``` 

# Synthetically remove Kt values

``` {r}
# Next we will sythetically remove observations based off the ratio of missing values for Kt.observed calculated below
statsNA(Kt.observed)

# create vector of NA statistics
na = c(rep(1, 392), rep(2, 120), rep(3, 180), rep(4, 219), rep(5, 57), rep(6, 11), rep(7,4), 9)
summary(na) #view summary statistics

set.seed(100) #set random seedfor reproducible results

# randomly mix up vector of NA statistics
ratio = sample(na)

# get indices of non-null values of Kt.observed and sample 783 points
non.na = which(!is.na(Kt.observed))
index = sample(non.na, length(na), replace = FALSE) #sample indices

Kt = Kt.observed #create Kt variable

#replace sample points wtih consecutive na points based on ratio
for (i in 1:length(ratio)){
  Kt = replace(Kt, list = index[i]:(index[i]+ratio[i]-1), rep(NA, ratio[i]))
}

# Sanity check
summary(Kt.observed)
# Kt is syntethic set of missing observations
summary(Kt)

#Visualization first 100 observations of Kt series
plot.ts(Kt[1:1000], ylab = "Kt")
```

# Set up bins to partition statistics

``` {r}
ratio.expand = vector()
index.list = vector()

#creates the strings of NA's based off a random starting indeces found above via sampling
for (i in 1:length(ratio)){
  index.list = append(index.list, index[i]:(index[i]+ratio[i]-1))
  ratio.expand = append(ratio.expand, rep(ratio[i], each = ratio[i]))
}

na.matrix = matrix(c(ratio.expand, index.list), ncol = 2) #all NA's
na.sorted = na.matrix[order(na.matrix[,1]),] #sorted NA's by length with corresponding indices
na.sorted = as.data.frame(na.sorted)
 
k1 = detect_index(na.sorted$V1, function(x){x > 1}) #detect indices for lengths of string of NA sizes
k2 = detect_index(na.sorted$V1, function(x){x > 2})
k3 = detect_index(na.sorted$V1, function(x){x > 3})
j = length(na.sorted$V1)

bin1 = na.sorted[1:(k2-1),2] #bin one includes 1 and 2 consecutive na's
na1 = which(is.na(Kt.observed[bin1])) #remove overlapping indices of true missing values from the values to sythetically remove
bin1 = bin1[-na1]

bin2 = na.sorted[k2:j, 2] #bin two includes 3 + consecutive na's
na2 = which(is.na(Kt.observed[bin2]))
bin2 = bin2[-na2]

bin3 = na.sorted[1:(k3-1),2] #bin three inclueds 1-3 consecutive na's
na3 = which(is.na(Kt.observed[bin3]))
bin3 = bin3[-na3]

bin4 = na.sorted[k3:j, 2] #bin four includes 4 + consecutive na's
na4 = which(is.na(Kt.observed[bin4]))
bin4 = bin4[-na4]

bin5 = na.sorted[1:(k1-1),2] #bin five includes singular na values
na5 = which(is.na(Kt.observed[bin5])) #there are no overlapping indices so we do not have any indices to remove from bin5
#bin5 = bin5[-na5]

bin6 = na.sorted[k1:j, 2] #bin six includes 2+ consecutive na's
na6 = which(is.na(Kt.observed[bin6]))
bin6 = bin2[-na6]
```


# Example 1.1: Perform imputation with KalmanSmoother and using a structural model fitted by maximum likelihood

``` {r}
ind = which(!is.na(Kt.observed)) #set indices for non-missing vales of original time series of KT

Kt_filled1 = na_kalman(Kt, 
                        model = "StructTS", smooth = TRUE)
```

``` {r}

# Calculate MBE, MBE%, RMSE, RMSE%, MAPE, and MAPE% for each bin for the method


# bin 1

MBE1.1 = mean(Kt_filled1[bin1] - Kt.observed[bin1])
MBE_p1.1 = (mean(Kt_filled1[bin1] - Kt.observed[bin1])/mean(Kt.observed[bin1]))*100

RMSE1.1 = sqrt(mean((Kt_filled1[bin1] - Kt.observed[bin1])^2))
RMSE_p1.1 = sqrt((mean((Kt_filled1[bin1] - Kt.observed[bin1])^2))/(mean((Kt.observed[bin1])^2)))*100

MAE1.1 = mean(abs(Kt_filled1[bin1] - Kt.observed[bin1]))
MAE_p1.1 = (mean(abs(Kt_filled1[bin1] - Kt.observed[bin1]))/mean(Kt.observed[bin1]))*100

# bin 2

MBE1.2 = mean(Kt_filled1[bin2] - Kt.observed[bin2])
MBE_p1.2 = (mean(Kt_filled1[bin2] - Kt.observed[bin2])/mean(Kt.observed[bin2]))*100

RMSE1.2 = sqrt(mean((Kt_filled1[bin2] - Kt.observed[bin2])^2))
RMSE_p1.2 = sqrt((mean((Kt_filled1[bin2] - Kt.observed[bin2])^2))/(mean((Kt.observed[bin2])^2)))*100

MAE1.2 = mean(abs(Kt_filled1[bin2] - Kt.observed[bin2]))
MAE_p1.2 = (mean(abs(Kt_filled1[bin2] - Kt.observed[bin2]))/mean(Kt.observed[bin2]))*100

# bin 3

MBE1.3 = mean(Kt_filled1[bin3] - Kt.observed[bin3])
MBE_p1.3 = (mean(Kt_filled1[bin3] - Kt.observed[bin3])/mean(Kt.observed[bin3]))*100

RMSE1.3 = sqrt(mean((Kt_filled1[bin3] - Kt.observed[bin3])^2))
RMSE_p1.3 = sqrt((mean((Kt_filled1[bin3] - Kt.observed[bin3])^2))/(mean((Kt.observed[bin3])^2)))*100

MAE1.3 = mean(abs(Kt_filled1[bin3] - Kt.observed[bin3]))
MAE_p1.3 = (mean(abs(Kt_filled1[bin3] - Kt.observed[bin3]))/mean(Kt.observed[bin3]))*100

# bin 4

MBE1.4 = mean(Kt_filled1[bin4] - Kt.observed[bin4])
MBE_p1.4 = (mean(Kt_filled1[bin4] - Kt.observed[bin4])/mean(Kt.observed[bin4]))*100

RMSE1.4 = sqrt(mean((Kt_filled1[bin4] - Kt.observed[bin4])^2))
RMSE_p1.4 = sqrt((mean((Kt_filled1[bin4] - Kt.observed[bin4])^2))/(mean((Kt.observed[bin4])^2)))*100

MAE1.4 = mean(abs(Kt_filled1[bin4] - Kt.observed[bin4]))
MAE_p1.4 = (mean(abs(Kt_filled1[bin4] - Kt.observed[bin4]))/mean(Kt.observed[bin4]))*100

# bin 5

MBE1.5 = mean(Kt_filled1[bin5] - Kt.observed[bin5])
MBE_p1.5 = (mean(Kt_filled1[bin5] - Kt.observed[bin5])/mean(Kt.observed[bin5]))*100

RMSE1.5 = sqrt(mean((Kt_filled1[bin5] - Kt.observed[bin5])^2))
RMSE_p1.5 = sqrt((mean((Kt_filled1[bin5] - Kt.observed[bin5])^2))/(mean((Kt.observed[bin5])^2)))*100

MAE1.5 = mean(abs(Kt_filled1[bin5] - Kt.observed[bin5]))
MAE_p1.5 = (mean(abs(Kt_filled1[bin5] - Kt.observed[bin5]))/mean(Kt.observed[bin5]))*100

# bin 6

MBE1.6 = mean(Kt_filled1[bin6] - Kt.observed[bin6])
MBE_p1.6 = (mean(Kt_filled1[bin6] - Kt.observed[bin6])/mean(Kt.observed[bin6]))*100

RMSE1.6 = sqrt(mean((Kt_filled1[bin6] - Kt.observed[bin6])^2))
RMSE_p1.6 = sqrt((mean((Kt_filled1[bin6] - Kt.observed[bin6])^2))/(mean((Kt.observed[bin6])^2)))*100

MAE1.6 = mean(abs(Kt_filled1[bin6] - Kt.observed[bin6]))
MAE_p1.6 = (mean(abs(Kt_filled1[bin6] - Kt.observed[bin6]))/mean(Kt.observed[bin6]))*100
```

# Example 1.2: Perform imputation with KalmanRun and state space representation of arima model

``` {r}
Kt_filled2 = na_kalman(Kt, 
                        model = "auto.arima", smooth = TRUE)
```

``` {r}
# bin 1

MBE2.1 = mean(Kt_filled2[bin1] - Kt.observed[bin1])
MBE_p2.1 = (mean(Kt_filled2[bin1] - Kt.observed[bin1])/mean(Kt.observed[bin1]))*100

RMSE2.1 = sqrt(mean((Kt_filled2[bin1] - Kt.observed[bin1])^2))
RMSE_p2.1 = sqrt((mean((Kt_filled2[bin1] - Kt.observed[bin1])^2))/(mean((Kt.observed[bin1])^2)))*100

MAE2.1 = mean(abs(Kt_filled2[bin1] - Kt.observed[bin1]))
MAE_p2.1 = (mean(abs(Kt_filled2[bin1] - Kt.observed[bin1]))/mean(Kt.observed[bin1]))*100

# bin 2

MBE2.2 = mean(Kt_filled2[bin2] - Kt.observed[bin2])
MBE_p2.2 = (mean(Kt_filled2[bin2] - Kt.observed[bin2])/mean(Kt.observed[bin2]))*100

RMSE2.2 = sqrt(mean((Kt_filled2[bin2] - Kt.observed[bin2])^2))
RMSE_p2.2 = sqrt((mean((Kt_filled2[bin2] - Kt.observed[bin2])^2))/(mean((Kt.observed[bin2])^2)))*100

MAE2.2 = mean(abs(Kt_filled2[bin2] - Kt.observed[bin2]))
MAE_p2.2 = (mean(abs(Kt_filled2[bin2] - Kt.observed[bin2]))/mean(Kt.observed[bin2]))*100

# bin 3

MBE2.3 = mean(Kt_filled2[bin3] - Kt.observed[bin3])
MBE_p2.3 = (mean(Kt_filled2[bin3] - Kt.observed[bin3])/mean(Kt.observed[bin3]))*100

RMSE2.3 = sqrt(mean((Kt_filled2[bin3] - Kt.observed[bin3])^2))
RMSE_p2.3 = sqrt((mean((Kt_filled2[bin3] - Kt.observed[bin3])^2))/(mean((Kt.observed[bin3])^2)))*100

MAE2.3 = mean(abs(Kt_filled2[bin3] - Kt.observed[bin3]))
MAE_p2.3 = (mean(abs(Kt_filled2[bin3] - Kt.observed[bin3]))/mean(Kt.observed[bin3]))*100

# bin 4

MBE2.4 = mean(Kt_filled2[bin4] - Kt.observed[bin4])
MBE_p2.4 = (mean(Kt_filled2[bin4] - Kt.observed[bin4])/mean(Kt.observed[bin4]))*100

RMSE2.4 = sqrt(mean((Kt_filled2[bin4] - Kt.observed[bin4])^2))
RMSE_p2.4 = sqrt((mean((Kt_filled2[bin4] - Kt.observed[bin4])^2))/(mean((Kt.observed[bin4])^2)))*100

MAE2.4 = mean(abs(Kt_filled2[bin4] - Kt.observed[bin4]))
MAE_p2.4 = (mean(abs(Kt_filled2[bin4] - Kt.observed[bin4]))/mean(Kt.observed[bin4]))*100

# bin 5

MBE2.5 = mean(Kt_filled2[bin5] - Kt.observed[bin5])
MBE_p2.5 = (mean(Kt_filled2[bin5] - Kt.observed[bin5])/mean(Kt.observed[bin5]))*100

RMSE2.5 = sqrt(mean((Kt_filled2[bin5] - Kt.observed[bin5])^2))
RMSE_p2.5 = sqrt((mean((Kt_filled2[bin5] - Kt.observed[bin5])^2))/(mean((Kt.observed[bin5])^2)))*100

MAE2.5 = mean(abs(Kt_filled2[bin5] - Kt.observed[bin5]))
MAE_p2.5 = (mean(abs(Kt_filled2[bin5] - Kt.observed[bin5]))/mean(Kt.observed[bin5]))*100

# bin 6

MBE2.6 = mean(Kt_filled2[bin6] - Kt.observed[bin6])
MBE_p2.6 = (mean(Kt_filled2[bin6] - Kt.observed[bin6])/mean(Kt.observed[bin6]))*100

RMSE2.6 = sqrt(mean((Kt_filled2[bin6] - Kt.observed[bin6])^2))
RMSE_p2.6 = sqrt((mean((Kt_filled2[bin6] - Kt.observed[bin6])^2))/(mean((Kt.observed[bin6])^2)))*100

MAE2.6 = mean(abs(Kt_filled2[bin6] - Kt.observed[bin6]))
MAE_p2.6 = (mean(abs(Kt_filled2[bin6] - Kt.observed[bin6]))/mean(Kt.observed[bin6]))*100
```

# Example 1.3: Perform imputation with KalmanSmooth and StructTS model with additional parameters

``` {r}
Kt_filled3 = na_kalman(Kt, 
                        model = "StructTS", smooth = TRUE, 
                        type = "trend")
```

``` {r}
# bin 1

MBE3.1 = mean(Kt_filled3[bin1] - Kt.observed[bin1])
MBE_p3.1 = (mean(Kt_filled3[bin1] - Kt.observed[bin1])/mean(Kt.observed[bin1]))*100

RMSE3.1 = sqrt(mean((Kt_filled3[bin1] - Kt.observed[bin1])^2))
RMSE_p3.1 = sqrt((mean((Kt_filled3[bin1] - Kt.observed[bin1])^2))/(mean((Kt.observed[bin1])^2)))*100

MAE3.1 = mean(abs(Kt_filled3[bin1] - Kt.observed[bin1]))
MAE_p3.1 = (mean(abs(Kt_filled3[bin1] - Kt.observed[bin1]))/mean(Kt.observed[bin1]))*100

# bin 2

MBE3.2 = mean(Kt_filled3[bin2] - Kt.observed[bin2])
MBE_p3.2 = (mean(Kt_filled3[bin2] - Kt.observed[bin2])/mean(Kt.observed[bin2]))*100

RMSE3.2 = sqrt(mean((Kt_filled3[bin2] - Kt.observed[bin2])^2))
RMSE_p3.2 = sqrt((mean((Kt_filled3[bin2] - Kt.observed[bin2])^2))/(mean((Kt.observed[bin2])^2)))*100

MAE3.2 = mean(abs(Kt_filled3[bin2] - Kt.observed[bin2]))
MAE_p3.2 = (mean(abs(Kt_filled3[bin2] - Kt.observed[bin2]))/mean(Kt.observed[bin2]))*100

# bin 3

MBE3.3 = mean(Kt_filled3[bin3] - Kt.observed[bin3])
MBE_p3.3 = (mean(Kt_filled3[bin3] - Kt.observed[bin3])/mean(Kt.observed[bin3]))*100

RMSE3.3 = sqrt(mean((Kt_filled3[bin3] - Kt.observed[bin3])^2))
RMSE_p3.3 = sqrt((mean((Kt_filled3[bin3] - Kt.observed[bin3])^2))/(mean((Kt.observed[bin3])^2)))*100

MAE3.3 = mean(abs(Kt_filled3[bin3] - Kt.observed[bin3]))
MAE_p3.3 = (mean(abs(Kt_filled3[bin3] - Kt.observed[bin3]))/mean(Kt.observed[bin3]))*100

# bin 4

MBE3.4 = mean(Kt_filled3[bin4] - Kt.observed[bin4])
MBE_p3.4 = (mean(Kt_filled3[bin4] - Kt.observed[bin4])/mean(Kt.observed[bin4]))*100

RMSE3.4 = sqrt(mean((Kt_filled3[bin4] - Kt.observed[bin4])^2))
RMSE_p3.4 = sqrt((mean((Kt_filled3[bin4] - Kt.observed[bin4])^2))/(mean((Kt.observed[bin4])^2)))*100

MAE3.4 = mean(abs(Kt_filled3[bin4] - Kt.observed[bin4]))
MAE_p3.4 = (mean(abs(Kt_filled3[bin4] - Kt.observed[bin4]))/mean(Kt.observed[bin4]))*100

# bin 5

MBE3.5 = mean(Kt_filled3[bin5] - Kt.observed[bin5])
MBE_p3.5 = (mean(Kt_filled3[bin5] - Kt.observed[bin5])/mean(Kt.observed[bin5]))*100

RMSE3.5 = sqrt(mean((Kt_filled3[bin5] - Kt.observed[bin5])^2))
RMSE_p3.5 = sqrt((mean((Kt_filled3[bin5] - Kt.observed[bin5])^2))/(mean((Kt.observed[bin5])^2)))*100

MAE3.5 = mean(abs(Kt_filled3[bin5] - Kt.observed[bin5]))
MAE_p3.5 = (mean(abs(Kt_filled3[bin5] - Kt.observed[bin5]))/mean(Kt.observed[bin5]))*100

# bin 6

MBE3.6 = mean(Kt_filled3[bin6] - Kt.observed[bin6])
MBE_p3.6 = (mean(Kt_filled3[bin6] - Kt.observed[bin6])/mean(Kt.observed[bin6]))*100

RMSE3.6 = sqrt(mean((Kt_filled3[bin6] - Kt.observed[bin6])^2))
RMSE_p3.6 = sqrt((mean((Kt_filled3[bin6] - Kt.observed[bin6])^2))/(mean((Kt.observed[bin6])^2)))*100

MAE3.6 = mean(abs(Kt_filled3[bin6] - Kt.observed[bin6]))
MAE_p3.6 = (mean(abs(Kt_filled3[bin6] - Kt.observed[bin6]))/mean(Kt.observed[bin6]))*100
```

# Example 2.1: Perform linear interpolation

``` {r}

Kt_filled4 = na_interpolation(Kt, 
                        option = "linear")

#ggplot_na_imputations(x.withNA = Kt[1:100], 
 #                  x.withImputations = Kt_filled4[1:100],
  #                 x.withTruth = Kt.observed[1:100], ylab = "Kt Value") 
summary(Kt.observed)
summary(Kt_filled4)

MSPE4 = mean((Kt.observed[ind] - Kt_filled4[ind])^2)
MAPE4 = mean(abs(Kt.observed[ind] - Kt_filled4[ind]))

MSPE4*1000
MAPE4*1000
```

``` {r}
# bin 1

MBE4.1 = mean(Kt_filled4[bin1] - Kt.observed[bin1])
MBE_p4.1 = (mean(Kt_filled4[bin1] - Kt.observed[bin1])/mean(Kt.observed[bin1]))*100

RMSE4.1 = sqrt(mean((Kt_filled4[bin1] - Kt.observed[bin1])^2))
RMSE_p4.1 = sqrt((mean((Kt_filled4[bin1] - Kt.observed[bin1])^2))/(mean((Kt.observed[bin1])^2)))*100

MAE4.1 = mean(abs(Kt_filled4[bin1] - Kt.observed[bin1]))
MAE_p4.1 = (mean(abs(Kt_filled4[bin1] - Kt.observed[bin1]))/mean(Kt.observed[bin1]))*100

# bin 2

MBE4.2 = mean(Kt_filled4[bin2] - Kt.observed[bin2])
MBE_p4.2 = (mean(Kt_filled4[bin2] - Kt.observed[bin2])/mean(Kt.observed[bin2]))*100

RMSE4.2 = sqrt(mean((Kt_filled4[bin2] - Kt.observed[bin2])^2))
RMSE_p4.2 = sqrt((mean((Kt_filled4[bin2] - Kt.observed[bin2])^2))/(mean((Kt.observed[bin2])^2)))*100

MAE4.2 = mean(abs(Kt_filled4[bin2] - Kt.observed[bin2]))
MAE_p4.2 = (mean(abs(Kt_filled4[bin2] - Kt.observed[bin2]))/mean(Kt.observed[bin2]))*100

# bin 3

MBE4.3 = mean(Kt_filled4[bin3] - Kt.observed[bin3])
MBE_p4.3 = (mean(Kt_filled4[bin3] - Kt.observed[bin3])/mean(Kt.observed[bin3]))*100

RMSE4.3 = sqrt(mean((Kt_filled4[bin3] - Kt.observed[bin3])^2))
RMSE_p4.3 = sqrt((mean((Kt_filled4[bin3] - Kt.observed[bin3])^2))/(mean((Kt.observed[bin3])^2)))*100

MAE4.3 = mean(abs(Kt_filled4[bin3] - Kt.observed[bin3]))
MAE_p4.3 = (mean(abs(Kt_filled4[bin3] - Kt.observed[bin3]))/mean(Kt.observed[bin3]))*100

#bin 4

MBE4.4 = mean(Kt_filled4[bin4] - Kt.observed[bin4])
MBE_p4.4 = (mean(Kt_filled4[bin4] - Kt.observed[bin4])/mean(Kt.observed[bin4]))*100

RMSE4.4 = sqrt(mean((Kt_filled4[bin4] - Kt.observed[bin4])^2))
RMSE_p4.4 = sqrt((mean((Kt_filled4[bin4] - Kt.observed[bin4])^2))/(mean((Kt.observed[bin4])^2)))*100

MAE4.4 = mean(abs(Kt_filled4[bin4] - Kt.observed[bin4]))
MAE_p4.4 = (mean(abs(Kt_filled4[bin4] - Kt.observed[bin4]))/mean(Kt.observed[bin4]))*100

# bin 5

MBE4.5 = mean(Kt_filled4[bin5] - Kt.observed[bin5])
MBE_p4.5 = (mean(Kt_filled4[bin5] - Kt.observed[bin5])/mean(Kt.observed[bin5]))*100

RMSE4.5 = sqrt(mean((Kt_filled4[bin5] - Kt.observed[bin5])^2))
RMSE_p4.5 = sqrt((mean((Kt_filled4[bin5] - Kt.observed[bin5])^2))/(mean((Kt.observed[bin5])^2)))*100

MAE4.5 = mean(abs(Kt_filled4[bin5] - Kt.observed[bin5]))
MAE_p4.5 = (mean(abs(Kt_filled4[bin5] - Kt.observed[bin5]))/mean(Kt.observed[bin5]))*100

# bin 6

MBE4.6 = mean(Kt_filled4[bin6] - Kt.observed[bin6])
MBE_p4.6 = (mean(Kt_filled4[bin6] - Kt.observed[bin6])/mean(Kt.observed[bin6]))*100

RMSE4.6 = sqrt(mean((Kt_filled4[bin6] - Kt.observed[bin6])^2))
RMSE_p4.6 = sqrt((mean((Kt_filled4[bin6] - Kt.observed[bin6])^2))/(mean((Kt.observed[bin6])^2)))*100

MAE4.6 = mean(abs(Kt_filled4[bin6] - Kt.observed[bin6]))
MAE_p4.6 = (mean(abs(Kt_filled4[bin6] - Kt.observed[bin6]))/mean(Kt.observed[bin6]))*100
```

# Example 2.2: Perform spline interpolation

``` {r}
Kt_filled5 = na_interpolation(Kt, 
                        option = "spline")
```

``` {r}
# bin 1

MBE5.1 = mean(Kt_filled5[bin1] - Kt.observed[bin1])
MBE_p5.1 = (mean(Kt_filled5[bin1] - Kt.observed[bin1])/mean(Kt.observed[bin1]))*100

RMSE5.1 = sqrt(mean((Kt_filled5[bin1] - Kt.observed[bin1])^2))
RMSE_p5.1 = sqrt((mean((Kt_filled5[bin1] - Kt.observed[bin1])^2))/(mean((Kt.observed[bin1])^2)))*100

MAE5.1 = mean(abs(Kt_filled5[bin1] - Kt.observed[bin1]))
MAE_p5.1 = (mean(abs(Kt_filled5[bin1] - Kt.observed[bin1]))/mean(Kt.observed[bin1]))*100

# bin 2

MBE5.2 = mean(Kt_filled5[bin2] - Kt.observed[bin2])
MBE_p5.2 = (mean(Kt_filled5[bin2] - Kt.observed[bin2])/mean(Kt.observed[bin2]))*100

RMSE5.2 = sqrt(mean((Kt_filled5[bin2] - Kt.observed[bin2])^2))
RMSE_p5.2 = sqrt((mean((Kt_filled5[bin2] - Kt.observed[bin2])^2))/(mean((Kt.observed[bin2])^2)))*100

MAE5.2 = mean(abs(Kt_filled5[bin2] - Kt.observed[bin2]))
MAE_p5.2 = (mean(abs(Kt_filled5[bin2] - Kt.observed[bin2]))/mean(Kt.observed[bin2]))*100

# bin 3

MBE5.3 = mean(Kt_filled5[bin3] - Kt.observed[bin3])
MBE_p5.3 = (mean(Kt_filled5[bin3] - Kt.observed[bin3])/mean(Kt.observed[bin3]))*100

RMSE5.3 = sqrt(mean((Kt_filled5[bin3] - Kt.observed[bin3])^2))
RMSE_p5.3 = sqrt((mean((Kt_filled5[bin3] - Kt.observed[bin3])^2))/(mean((Kt.observed[bin3])^2)))*100

MAE5.3 = mean(abs(Kt_filled5[bin3] - Kt.observed[bin3]))
MAE_p5.3 = (mean(abs(Kt_filled5[bin3] - Kt.observed[bin3]))/mean(Kt.observed[bin3]))*100

#bin 4

MBE5.4 = mean(Kt_filled5[bin4] - Kt.observed[bin4])
MBE_p5.4 = (mean(Kt_filled5[bin4] - Kt.observed[bin4])/mean(Kt.observed[bin4]))*100

RMSE5.4 = sqrt(mean((Kt_filled5[bin4] - Kt.observed[bin4])^2))
RMSE_p5.4 = sqrt((mean((Kt_filled5[bin4] - Kt.observed[bin4])^2))/(mean((Kt.observed[bin4])^2)))*100

MAE5.4 = mean(abs(Kt_filled5[bin4] - Kt.observed[bin4]))
MAE_p5.4 = (mean(abs(Kt_filled5[bin4] - Kt.observed[bin4]))/mean(Kt.observed[bin4]))*100

# bin 5

MBE5.5 = mean(Kt_filled5[bin5] - Kt.observed[bin5])
MBE_p5.5 = (mean(Kt_filled5[bin5] - Kt.observed[bin5])/mean(Kt.observed[bin5]))*100

RMSE5.5 = sqrt(mean((Kt_filled5[bin5] - Kt.observed[bin5])^2))
RMSE_p5.5 = sqrt((mean((Kt_filled5[bin5] - Kt.observed[bin5])^2))/(mean((Kt.observed[bin5])^2)))*100

MAE5.5 = mean(abs(Kt_filled5[bin5] - Kt.observed[bin5]))
MAE_p5.5 = (mean(abs(Kt_filled5[bin5] - Kt.observed[bin5]))/mean(Kt.observed[bin5]))*100

# bin 6

MBE5.6 = mean(Kt_filled5[bin6] - Kt.observed[bin6])
MBE_p5.6 = (mean(Kt_filled5[bin6] - Kt.observed[bin6])/mean(Kt.observed[bin6]))*100

RMSE5.6 = sqrt(mean((Kt_filled5[bin6] - Kt.observed[bin6])^2))
RMSE_p5.6 = sqrt((mean((Kt_filled5[bin6] - Kt.observed[bin6])^2))/(mean((Kt.observed[bin6])^2)))*100

MAE5.6 = mean(abs(Kt_filled5[bin6] - Kt.observed[bin6]))
MAE_p5.6 = (mean(abs(Kt_filled5[bin6] - Kt.observed[bin6]))/mean(Kt.observed[bin6]))*100
```

# Example 2.3: Perform stine interpolation

``` {r}
Kt_filled6 = na_interpolation(Kt, 
                        option = "stine")

#plotNA.imputations(x.withNA = Kt[1:100], 
#                   x.withImputations = Kt_filled6[1:100],
#                   x.withTruth = Kt.observed[1:100], ylab = "Kt Value") 

summary(Kt.observed)
summary(Kt_filled6)

MSPE6 = mean((Kt.observed[ind] - Kt_filled6[ind])^2)
MAPE6 = mean(abs(Kt.observed[ind] - Kt_filled6[ind]))

MSPE6*1000
MAPE6*1000
```


``` {r}
# bin 1

MBE6.1 = mean(Kt_filled6[bin1] - Kt.observed[bin1])
MBE_p6.1 = (mean(Kt_filled6[bin1] - Kt.observed[bin1])/mean(Kt.observed[bin1]))*100

RMSE6.1 = sqrt(mean((Kt_filled6[bin1] - Kt.observed[bin1])^2))
RMSE_p6.1 = sqrt((mean((Kt_filled6[bin1] - Kt.observed[bin1])^2))/(mean((Kt.observed[bin1])^2)))*100

MAE6.1 = mean(abs(Kt_filled6[bin1] - Kt.observed[bin1]))
MAE_p6.1 = (mean(abs(Kt_filled6[bin1] - Kt.observed[bin1]))/mean(Kt.observed[bin1]))*100

# bin 2

MBE6.2 = mean(Kt_filled6[bin2] - Kt.observed[bin2])
MBE_p6.2 = (mean(Kt_filled6[bin2] - Kt.observed[bin2])/mean(Kt.observed[bin2]))*100

RMSE6.2 = sqrt(mean((Kt_filled6[bin2] - Kt.observed[bin2])^2))
RMSE_p6.2 = sqrt((mean((Kt_filled6[bin2] - Kt.observed[bin2])^2))/(mean((Kt.observed[bin2])^2)))*100

MAE6.2 = mean(abs(Kt_filled6[bin2] - Kt.observed[bin2]))
MAE_p6.2 = (mean(abs(Kt_filled6[bin2] - Kt.observed[bin2]))/mean(Kt.observed[bin2]))*100

# bin 3

MBE6.3 = mean(Kt_filled6[bin3] - Kt.observed[bin3])
MBE_p6.3 = (mean(Kt_filled6[bin3] - Kt.observed[bin3])/mean(Kt.observed[bin3]))*100

RMSE6.3 = sqrt(mean((Kt_filled6[bin3] - Kt.observed[bin3])^2))
RMSE_p6.3 = sqrt((mean((Kt_filled6[bin3] - Kt.observed[bin3])^2))/(mean((Kt.observed[bin3])^2)))*100

MAE6.3 = mean(abs(Kt_filled6[bin3] - Kt.observed[bin3]))
MAE_p6.3 = (mean(abs(Kt_filled6[bin3] - Kt.observed[bin3]))/mean(Kt.observed[bin3]))*100

# bin 4

MBE6.4 = mean(Kt_filled6[bin4] - Kt.observed[bin4])
MBE_p6.4 = (mean(Kt_filled6[bin4] - Kt.observed[bin4])/mean(Kt.observed[bin4]))*100

RMSE6.4 = sqrt(mean((Kt_filled6[bin4] - Kt.observed[bin4])^2))
RMSE_p6.4 = sqrt((mean((Kt_filled6[bin4] - Kt.observed[bin4])^2))/(mean((Kt.observed[bin4])^2)))*100

MAE6.4 = mean(abs(Kt_filled6[bin4] - Kt.observed[bin4]))
MAE_p6.4 = (mean(abs(Kt_filled6[bin4] - Kt.observed[bin4]))/mean(Kt.observed[bin4]))*100

# bin 5

MBE6.5 = mean(Kt_filled6[bin5] - Kt.observed[bin5])
MBE_p6.5 = (mean(Kt_filled6[bin5] - Kt.observed[bin5])/mean(Kt.observed[bin5]))*100

RMSE6.5 = sqrt(mean((Kt_filled6[bin5] - Kt.observed[bin5])^2))
RMSE_p6.5 = sqrt((mean((Kt_filled6[bin5] - Kt.observed[bin5])^2))/(mean((Kt.observed[bin5])^2)))*100

MAE6.5 = mean(abs(Kt_filled6[bin5] - Kt.observed[bin5]))
MAE_p6.5 = (mean(abs(Kt_filled6[bin5] - Kt.observed[bin5]))/mean(Kt.observed[bin5]))*100

# bin 6

MBE6.6 = mean(Kt_filled6[bin6] - Kt.observed[bin6])
MBE_p6.6 = (mean(Kt_filled6[bin6] - Kt.observed[bin6])/mean(Kt.observed[bin6]))*100

RMSE6.6 = sqrt(mean((Kt_filled6[bin6] - Kt.observed[bin6])^2))
RMSE_p6.6 = sqrt((mean((Kt_filled6[bin6] - Kt.observed[bin6])^2))/(mean((Kt.observed[bin6])^2)))*100

MAE6.6 = mean(abs(Kt_filled6[bin6] - Kt.observed[bin6]))
MAE_p6.6 = (mean(abs(Kt_filled6[bin6] - Kt.observed[bin6]))/mean(Kt.observed[bin6]))*100
```


# Example 4.1: Perform imputation with simple moving average

``` {r}
# default

Kt_filled9 = na_ma(Kt, weighting = "simple")
```

``` {r}
# bin 1

MBE9.1 = mean(Kt_filled9[bin1] - Kt.observed[bin1])
MBE_p9.1 = (mean(Kt_filled9[bin1] - Kt.observed[bin1])/mean(Kt.observed[bin1]))*100

RMSE9.1 = sqrt(mean((Kt_filled9[bin1] - Kt.observed[bin1])^2))
RMSE_p9.1 = sqrt((mean((Kt_filled9[bin1] - Kt.observed[bin1])^2))/(mean((Kt.observed[bin1])^2)))*100

MAE9.1 = mean(abs(Kt_filled9[bin1] - Kt.observed[bin1]))
MAE_p9.1 = (mean(abs(Kt_filled9[bin1] - Kt.observed[bin1]))/mean(Kt.observed[bin1]))*100

# bin 2

MBE9.2 = mean(Kt_filled9[bin2] - Kt.observed[bin2])
MBE_p9.2 = (mean(Kt_filled9[bin2] - Kt.observed[bin2])/mean(Kt.observed[bin2]))*100

RMSE9.2 = sqrt(mean((Kt_filled9[bin2] - Kt.observed[bin2])^2))
RMSE_p9.2 = sqrt((mean((Kt_filled9[bin2] - Kt.observed[bin2])^2))/(mean((Kt.observed[bin2])^2)))*100

MAE9.2 = mean(abs(Kt_filled9[bin2] - Kt.observed[bin2]))
MAE_p9.2 = (mean(abs(Kt_filled9[bin2] - Kt.observed[bin2]))/mean(Kt.observed[bin2]))*100

# bin 3

MBE9.3 = mean(Kt_filled9[bin3] - Kt.observed[bin3])
MBE_p9.3 = (mean(Kt_filled9[bin3] - Kt.observed[bin3])/mean(Kt.observed[bin3]))*100

RMSE9.3 = sqrt(mean((Kt_filled9[bin3] - Kt.observed[bin3])^2))
RMSE_p9.3 = sqrt((mean((Kt_filled9[bin3] - Kt.observed[bin3])^2))/(mean((Kt.observed[bin3])^2)))*100

MAE9.3 = mean(abs(Kt_filled9[bin3] - Kt.observed[bin3]))
MAE_p9.3 = (mean(abs(Kt_filled9[bin3] - Kt.observed[bin3]))/mean(Kt.observed[bin3]))*100

# bin 4

MBE9.4 = mean(Kt_filled9[bin4] - Kt.observed[bin4])
MBE_p9.4 = (mean(Kt_filled9[bin4] - Kt.observed[bin4])/mean(Kt.observed[bin4]))*100

RMSE9.4 = sqrt(mean((Kt_filled9[bin4] - Kt.observed[bin4])^2))
RMSE_p9.4 = sqrt((mean((Kt_filled9[bin4] - Kt.observed[bin4])^2))/(mean((Kt.observed[bin4])^2)))*100

MAE9.4 = mean(abs(Kt_filled9[bin4] - Kt.observed[bin4]))
MAE_p9.4 = (mean(abs(Kt_filled9[bin4] - Kt.observed[bin4]))/mean(Kt.observed[bin4]))*100

# bin 5

MBE9.5 = mean(Kt_filled9[bin5] - Kt.observed[bin5])
MBE_p9.5 = (mean(Kt_filled9[bin5] - Kt.observed[bin5])/mean(Kt.observed[bin5]))*100

RMSE9.5 = sqrt(mean((Kt_filled9[bin5] - Kt.observed[bin5])^2))
RMSE_p9.5 = sqrt((mean((Kt_filled9[bin5] - Kt.observed[bin5])^2))/(mean((Kt.observed[bin5])^2)))*100

MAE9.5 = mean(abs(Kt_filled9[bin5] - Kt.observed[bin5]))
MAE_p9.5 = (mean(abs(Kt_filled9[bin5] - Kt.observed[bin5]))/mean(Kt.observed[bin5]))*100

# bin 6

MBE9.6 = mean(Kt_filled9[bin6] - Kt.observed[bin6])
MBE_p9.6 = (mean(Kt_filled9[bin6] - Kt.observed[bin6])/mean(Kt.observed[bin6]))*100

RMSE9.6 = sqrt(mean((Kt_filled9[bin6] - Kt.observed[bin6])^2))
RMSE_p9.6 = sqrt((mean((Kt_filled9[bin6] - Kt.observed[bin6])^2))/(mean((Kt.observed[bin6])^2)))*100

MAE9.6 = mean(abs(Kt_filled9[bin6] - Kt.observed[bin6]))
MAE_p9.6 = (mean(abs(Kt_filled9[bin6] - Kt.observed[bin6]))/mean(Kt.observed[bin6]))*100
```

# Example 4.2: Perform imputation with linear weighted moving average

``` {r}
# default

Kt_filled10 = na_ma(Kt, weighting = "linear")
```


``` {r}
# bin 1

MBE10.1 = mean(Kt_filled10[bin1] - Kt.observed[bin1])
MBE_p10.1 = (mean(Kt_filled10[bin1] - Kt.observed[bin1])/mean(Kt.observed[bin1]))*100

RMSE10.1 = sqrt(mean((Kt_filled10[bin1] - Kt.observed[bin1])^2))
RMSE_p10.1 = sqrt((mean((Kt_filled10[bin1] - Kt.observed[bin1])^2))/(mean((Kt.observed[bin1])^2)))*100

MAE10.1 = mean(abs(Kt_filled10[bin1] - Kt.observed[bin1]))
MAE_p10.1 = (mean(abs(Kt_filled10[bin1] - Kt.observed[bin1]))/mean(Kt.observed[bin1]))*100

# bin 2

MBE10.2 = mean(Kt_filled10[bin2] - Kt.observed[bin2])
MBE_p10.2 = (mean(Kt_filled10[bin2] - Kt.observed[bin2])/mean(Kt.observed[bin2]))*100

RMSE10.2 = sqrt(mean((Kt_filled10[bin2] - Kt.observed[bin2])^2))
RMSE_p10.2 = sqrt((mean((Kt_filled10[bin2] - Kt.observed[bin2])^2))/(mean((Kt.observed[bin2])^2)))*100

MAE10.2 = mean(abs(Kt_filled10[bin2] - Kt.observed[bin2]))
MAE_p10.2 = (mean(abs(Kt_filled10[bin2] - Kt.observed[bin2]))/mean(Kt.observed[bin2]))*100

# bin 3

MBE10.3 = mean(Kt_filled10[bin3] - Kt.observed[bin3])
MBE_p10.3 = (mean(Kt_filled10[bin3] - Kt.observed[bin3])/mean(Kt.observed[bin3]))*100

RMSE10.3 = sqrt(mean((Kt_filled10[bin3] - Kt.observed[bin3])^2))
RMSE_p10.3 = sqrt((mean((Kt_filled10[bin3] - Kt.observed[bin3])^2))/(mean((Kt.observed[bin3])^2)))*100

MAE10.3 = mean(abs(Kt_filled10[bin3] - Kt.observed[bin3]))
MAE_p10.3 = (mean(abs(Kt_filled10[bin3] - Kt.observed[bin3]))/mean(Kt.observed[bin3]))*100

# bin 4

MBE10.4 = mean(Kt_filled10[bin4] - Kt.observed[bin4])
MBE_p10.4 = (mean(Kt_filled10[bin4] - Kt.observed[bin4])/mean(Kt.observed[bin4]))*100

RMSE10.4 = sqrt(mean((Kt_filled10[bin4] - Kt.observed[bin4])^2))
RMSE_p10.4 = sqrt((mean((Kt_filled10[bin4] - Kt.observed[bin4])^2))/(mean((Kt.observed[bin4])^2)))*100

MAE10.4 = mean(abs(Kt_filled10[bin4] - Kt.observed[bin4]))
MAE_p10.4 = (mean(abs(Kt_filled10[bin4] - Kt.observed[bin4]))/mean(Kt.observed[bin4]))*100

# bin 5

MBE10.5 = mean(Kt_filled10[bin5] - Kt.observed[bin5])
MBE_p10.5 = (mean(Kt_filled10[bin5] - Kt.observed[bin5])/mean(Kt.observed[bin5]))*100

RMSE10.5 = sqrt(mean((Kt_filled10[bin5] - Kt.observed[bin5])^2))
RMSE_p10.5 = sqrt((mean((Kt_filled10[bin5] - Kt.observed[bin5])^2))/(mean((Kt.observed[bin5])^2)))*100

MAE10.5 = mean(abs(Kt_filled10[bin5] - Kt.observed[bin5]))
MAE_p10.5 = (mean(abs(Kt_filled10[bin5] - Kt.observed[bin5]))/mean(Kt.observed[bin5]))*100

# bin 6

MBE10.6 = mean(Kt_filled10[bin6] - Kt.observed[bin6])
MBE_p10.6 = (mean(Kt_filled10[bin6] - Kt.observed[bin6])/mean(Kt.observed[bin6]))*100

RMSE10.6 = sqrt(mean((Kt_filled10[bin6] - Kt.observed[bin6])^2))
RMSE_p10.6 = sqrt((mean((Kt_filled10[bin6] - Kt.observed[bin6])^2))/(mean((Kt.observed[bin6])^2)))*100

MAE10.6 = mean(abs(Kt_filled10[bin6] - Kt.observed[bin6]))
MAE_p10.6 = (mean(abs(Kt_filled10[bin6] - Kt.observed[bin6]))/mean(Kt.observed[bin6]))*100
```

# Example 4.3: Perform imputation with exponential weighted moving average

``` {r}
# default

Kt_filled11 = na_ma(Kt, weighting = "exponential")
```

``` {r}
# bin 1

MBE11.1 = mean(Kt_filled11[bin1] - Kt.observed[bin1])
MBE_p11.1 = (mean(Kt_filled11[bin1] - Kt.observed[bin1])/mean(Kt.observed[bin1]))*100

RMSE11.1 = sqrt(mean((Kt_filled11[bin1] - Kt.observed[bin1])^2))
RMSE_p11.1 = sqrt((mean((Kt_filled11[bin1] - Kt.observed[bin1])^2))/(mean((Kt.observed[bin1])^2)))*100

MAE11.1 = mean(abs(Kt_filled11[bin1] - Kt.observed[bin1]))
MAE_p11.1 = (mean(abs(Kt_filled11[bin1] - Kt.observed[bin1]))/mean(Kt.observed[bin1]))*100

# bin 2

MBE11.2 = mean(Kt_filled11[bin2] - Kt.observed[bin2])
MBE_p11.2 = (mean(Kt_filled11[bin2] - Kt.observed[bin2])/mean(Kt.observed[bin2]))*100

RMSE11.2 = sqrt(mean((Kt_filled11[bin2] - Kt.observed[bin2])^2))
RMSE_p11.2 = sqrt((mean((Kt_filled11[bin2] - Kt.observed[bin2])^2))/(mean((Kt.observed[bin2])^2)))*100

MAE11.2 = mean(abs(Kt_filled11[bin2] - Kt.observed[bin2]))
MAE_p11.2 = (mean(abs(Kt_filled11[bin2] - Kt.observed[bin2]))/mean(Kt.observed[bin2]))*100

# bin 3

MBE11.3 = mean(Kt_filled11[bin3] - Kt.observed[bin3])
MBE_p11.3 = (mean(Kt_filled11[bin3] - Kt.observed[bin3])/mean(Kt.observed[bin3]))*100

RMSE11.3 = sqrt(mean((Kt_filled11[bin3] - Kt.observed[bin3])^2))
RMSE_p11.3 = sqrt((mean((Kt_filled11[bin3] - Kt.observed[bin3])^2))/(mean((Kt.observed[bin3])^2)))*100

MAE11.3 = mean(abs(Kt_filled11[bin3] - Kt.observed[bin3]))
MAE_p11.3 = (mean(abs(Kt_filled11[bin3] - Kt.observed[bin3]))/mean(Kt.observed[bin3]))*100

# bin 4

MBE11.4 = mean(Kt_filled11[bin4] - Kt.observed[bin4])
MBE_p11.4 = (mean(Kt_filled11[bin4] - Kt.observed[bin4])/mean(Kt.observed[bin4]))*100

RMSE11.4 = sqrt(mean((Kt_filled11[bin4] - Kt.observed[bin4])^2))
RMSE_p11.4 = sqrt((mean((Kt_filled11[bin4] - Kt.observed[bin4])^2))/(mean((Kt.observed[bin4])^2)))*100

MAE11.4 = mean(abs(Kt_filled11[bin4] - Kt.observed[bin4]))
MAE_p11.4 = (mean(abs(Kt_filled11[bin4] - Kt.observed[bin4]))/mean(Kt.observed[bin4]))*100

# bin 5

MBE11.5 = mean(Kt_filled11[bin5] - Kt.observed[bin5])
MBE_p11.5 = (mean(Kt_filled11[bin5] - Kt.observed[bin5])/mean(Kt.observed[bin5]))*100

RMSE11.5 = sqrt(mean((Kt_filled11[bin5] - Kt.observed[bin5])^2))
RMSE_p11.5 = sqrt((mean((Kt_filled11[bin5] - Kt.observed[bin5])^2))/(mean((Kt.observed[bin5])^2)))*100

MAE11.5 = mean(abs(Kt_filled11[bin5] - Kt.observed[bin5]))
MAE_p11.5 = (mean(abs(Kt_filled11[bin5] - Kt.observed[bin5]))/mean(Kt.observed[bin5]))*100

# bin 6

MBE11.6 = mean(Kt_filled11[bin6] - Kt.observed[bin6])
MBE_p11.6 = (mean(Kt_filled11[bin6] - Kt.observed[bin6])/mean(Kt.observed[bin6]))*100

RMSE11.6 = sqrt(mean((Kt_filled11[bin6] - Kt.observed[bin6])^2))
RMSE_p11.6 = sqrt((mean((Kt_filled11[bin6] - Kt.observed[bin6])^2))/(mean((Kt.observed[bin6])^2)))*100

MAE11.6 = mean(abs(Kt_filled11[bin6] - Kt.observed[bin6]))
MAE_p11.6 = (mean(abs(Kt_filled11[bin6] - Kt.observed[bin6]))/mean(Kt.observed[bin6]))*100
```

# Print the values for each bin size for stine and linear interpolation

``` {r}
RMSE = cbind(rbind(round(RMSE4.1, 4), round(RMSE4.2, 4), round(RMSE4.3, 4), round(RMSE4.4, 4), round(RMSE4.5, 4), round(RMSE4.6, 4)), rbind(round(RMSE6.1, 4), round(RMSE6.2, 4), round(RMSE6.3, 4), round(RMSE6.4, 4), round(RMSE6.5, 4), round(RMSE6.6, 4)))

RMSE_p = cbind(rbind(round(RMSE_p4.1, 1), round(RMSE_p4.2, 1), round(RMSE_p4.3, 1), round(RMSE_p4.4, 1), round(RMSE_p4.5, 1), round(RMSE_p4.6, 1)), rbind(round(RMSE_p6.1, 1), round(RMSE_p6.2, 1), round(RMSE_p6.3, 1), round(RMSE_p6.4, 1), round(RMSE_p6.5, 1), round(RMSE_p6.6, 1)))

MAE = cbind(rbind(round(MAE4.1, 4), round(MAE4.2, 4), round(MAE4.3, 4), round(MAE4.4, 4), round(MAE4.5, 4), round(MAE4.6, 4)), rbind(round(MAE6.1, 4), round(MAE6.2, 4), round(MAE6.3, 4), round(MAE6.4, 4), round(MAE6.5, 5), round(MAE6.6, 4)))

MAE_p = cbind(rbind(round(MAE_p4.1, 1), round(MAE_p4.2, 1), round(MAE_p4.3, 1), round(MAE_p4.4, 1), round(MAE_p4.5, 1), round(MAE_p4.6, 1)), rbind(round(MAE_p6.1, 1), round(MAE_p6.2, 1), round(MAE_p6.3, 1), round(MAE_p6.4, 1), round(MAE_p6.5, 2), round(MAE_p6.6, 1)))

MBE = cbind(rbind(round(MBE4.1, 6), round(MBE4.2, 6), round(MBE4.3, 6), round(MBE4.4, 6), round(MBE4.5, 6), round(MBE4.6, 6)), rbind(round(MBE6.1, 6), round(MBE6.2, 6), round(MBE6.3, 6), round(MBE6.4, 6), round(MBE6.5, 6), round(MBE6.6, 6)))

MBE_p = cbind(rbind(round(MBE_p4.1, 4), round(MBE_p4.2, 4), round(MBE_p4.3, 4), round(MBE_p4.4, 4), round(MBE_p4.5, 4), round(MBE_p4.6, 4)), rbind(round(MBE_p6.1, 4), round(MBE_p6.2, 4), round(MBE_p6.3, 4), round(MBE_p6.4, 4), round(MBE_p6.5, 4), round(MBE_p6.6, 4)))

RMSE
RMSE_p
MAE
MAE_p
MBE
MBE_p
```
