---
title: "FPK-SAT"
author: "Alexis Denhard"
date: "November 4, 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list = ls()) #clear environment
library(astsa)
library(imputeTS)
library(forecast)
library(fields)
```

``` {r}
library(lubridate) #yday function
library(iemisc) #cosd function

csdat2017 = suppressWarnings(read.csv("D:/Work/2017_data/FPK/FPK_48.29-105.06.csv"
                                      , header = TRUE)) 

#Remove first four NA rowws
csdat2017 = csdat2017[-1,]
csdat2017 = csdat2017[-1,]
csdat2017 = csdat2017[-1,]
csdat2017 = csdat2017[-1,]

#doy - day of year
df = as.Date(csdat2017$time_index)
doy = yday(df)
summary(doy)

B = 2*pi*doy/365
Rfact2 = 1.00011 + 0.034221 * cos(B)+ 0.00128*sin(B)+ 0.000719*cos(2*B)+0.000077*sin(2*B)

#extraterrestrial irradiance
ETRN = 1361*Rfact2

SZA = csdat2017$solar_zenith_angle

#set values to null for fill flag criteria
csdat2017 = within(csdat2017, ghi[fill_flag != 0] <- NA)
ghi = csdat2017$ghi

Kt = ghi / (ETRN * cosd(SZA))

Kt.observed = as.ts(Kt)

plot.ts(Kt.observed[1:1000], ylab = "Kt Observed")

index = which(is.na(Kt.observed))
``` 

``` {r}

# Next we will remove 2000 observations based off the ratio of missing values for Kt.observed
statsNA(Kt.observed)

```

``` {r}
# create vector of statistics
na = c(rep(1, 402), rep(2, 139), rep(3, 82), rep(4, 205), rep(5, 71), rep(6, 41), rep(7, 21), rep(8,6), rep(9,2), 10, rep(11,2), rep(12,2), rep(13,5), 14, rep(15,5), rep(16,6), 17, 18)
summary(na)

set.seed(100)

# randomly mix up vector
ratio = sample(na)

# get indices of non null values of Kt.observed and sample 783 points
non.na = which(!is.na(Kt.observed))
index = sample(non.na, 
               993, replace = FALSE) 

Kt = Kt.observed

#replace sample points wtih consecutive na points based on ratio
for (i in 1:length(ratio)){
  Kt = replace(Kt, list = index[i]:(index[i]+ratio[i]-1), rep(NA, ratio[i]))
}

#Kt.observed = replace(Kt.observed, list = index[1]:(index[1]+ratio[1]-1), rep(NA, ratio[1]))

summary(Kt.observed)
# Kt is syntethic set of missing observations
summary(Kt)

plot.ts(Kt[1:1000], ylab = "Kt")
```

# Set up bins to partition statistics

``` {r}
ratio.expand = vector()
index.list = vector()

for (i in 1:length(ratio)){
  index.list = append(index.list, index[i]:(index[i]+ratio[i]-1))
  ratio.expand = append(ratio.expand, rep(ratio[i], each = ratio[i]))
}

na.matrix = matrix(c(ratio.expand, index.list), ncol = 2)
na.sorted = na.matrix[order(na.matrix[,1]),]

bin1 = na.sorted[1:680,2] #bin one includes 1 and 2 consecutive na's
na1 = which(is.na(Kt.observed[bin1]))
bin1 = bin1[-na1]

bin2 = na.sorted[681:2901, 2] #bin two includes 3 + consecutive na's
summary(Kt.observed[bin2])
na2 = which(is.na(Kt.observed[bin2]))
bin2 = bin2[-na2]

bin3 = na.sorted[1:926,2] #bin three inclueds 1-3 consecutive na's
summary(Kt.observed[bin3])
na3 = which(is.na(Kt.observed[bin3]))
bin3 = bin3[-na3]

bin4 = na.sorted[927:2901, 2] #bin four includes 4 + consecutive na's
summary(Kt.observed[bin4])
na4 = which(is.na(Kt.observed[bin4]))
bin4 = bin4[-na4]

bin5 = na.sorted[1:402,2] #bin five includes singular na values
summary(Kt.observed[bin5])
na5 = which(is.na(Kt.observed[bin5]))
#bin5 = bin5[-na5]

bin6 = na.sorted[403:2901, 2] #bin six includes 2+ consecutive na's
summary(Kt.observed[bin6])
na6 = which(is.na(Kt.observed[bin6]))
bin6 = bin2[-na6]
```


# Example 1.1: Perform imputation with KalmanSmoother and using a structural model fitted by maximum likelihood

``` {r}
ind = which(!is.na(Kt.observed))

Kt_filled1 = na_kalman(Kt, 
                        model = "StructTS", smooth = TRUE)
```

``` {r}
# bin 1

MBE1.1 = mean(Kt_filled1[bin1] - Kt.observed[bin1])
MBE_p1.1 = (mean(Kt_filled1[bin1] - Kt.observed[bin1])/mean(Kt.observed[bin1]))*100

RMSE1.1 = sqrt(mean((Kt_filled1[bin1] - Kt.observed[bin1])^2))
RMSE_p1.1 = sqrt((mean((Kt_filled1[bin1] - Kt.observed[bin1])^2))/(mean((Kt.observed[bin1])^2)))*100

MAE1.1 = mean(abs(Kt_filled1[bin1] - Kt.observed[bin1]))
MAE_p1.1 = (mean(abs(Kt_filled1[bin1] - Kt.observed[bin1]))/mean(Kt.observed[bin1]))*100

# bin 2

MBE1.2 = mean(Kt_filled1[bin2] - Kt.observed[bin2])
MBE_p1.2 = (mean(Kt_filled1[bin2] - Kt.observed[bin2])/mean(Kt.observed[bin2]))*100

RMSE1.2 = sqrt(mean((Kt_filled1[bin2] - Kt.observed[bin2])^2))
RMSE_p1.2 = sqrt((mean((Kt_filled1[bin2] - Kt.observed[bin2])^2))/(mean((Kt.observed[bin2])^2)))*100

MAE1.2 = mean(abs(Kt_filled1[bin2] - Kt.observed[bin2]))
MAE_p1.2 = (mean(abs(Kt_filled1[bin2] - Kt.observed[bin2]))/mean(Kt.observed[bin2]))*100

# bin 3

MBE1.3 = mean(Kt_filled1[bin3] - Kt.observed[bin3])
MBE_p1.3 = (mean(Kt_filled1[bin3] - Kt.observed[bin3])/mean(Kt.observed[bin3]))*100

RMSE1.3 = sqrt(mean((Kt_filled1[bin3] - Kt.observed[bin3])^2))
RMSE_p1.3 = sqrt((mean((Kt_filled1[bin3] - Kt.observed[bin3])^2))/(mean((Kt.observed[bin3])^2)))*100

MAE1.3 = mean(abs(Kt_filled1[bin3] - Kt.observed[bin3]))
MAE_p1.3 = (mean(abs(Kt_filled1[bin3] - Kt.observed[bin3]))/mean(Kt.observed[bin3]))*100

# bin 4

MBE1.4 = mean(Kt_filled1[bin4] - Kt.observed[bin4])
MBE_p1.4 = (mean(Kt_filled1[bin4] - Kt.observed[bin4])/mean(Kt.observed[bin4]))*100

RMSE1.4 = sqrt(mean((Kt_filled1[bin4] - Kt.observed[bin4])^2))
RMSE_p1.4 = sqrt((mean((Kt_filled1[bin4] - Kt.observed[bin4])^2))/(mean((Kt.observed[bin4])^2)))*100

MAE1.4 = mean(abs(Kt_filled1[bin4] - Kt.observed[bin4]))
MAE_p1.4 = (mean(abs(Kt_filled1[bin4] - Kt.observed[bin4]))/mean(Kt.observed[bin4]))*100

# bin 5

MBE1.5 = mean(Kt_filled1[bin5] - Kt.observed[bin5])
MBE_p1.5 = (mean(Kt_filled1[bin5] - Kt.observed[bin5])/mean(Kt.observed[bin5]))*100

RMSE1.5 = sqrt(mean((Kt_filled1[bin5] - Kt.observed[bin5])^2))
RMSE_p1.5 = sqrt((mean((Kt_filled1[bin5] - Kt.observed[bin5])^2))/(mean((Kt.observed[bin5])^2)))*100

MAE1.5 = mean(abs(Kt_filled1[bin5] - Kt.observed[bin5]))
MAE_p1.5 = (mean(abs(Kt_filled1[bin5] - Kt.observed[bin5]))/mean(Kt.observed[bin5]))*100

# bin 6

MBE1.6 = mean(Kt_filled1[bin6] - Kt.observed[bin6])
MBE_p1.6 = (mean(Kt_filled1[bin6] - Kt.observed[bin6])/mean(Kt.observed[bin6]))*100

RMSE1.6 = sqrt(mean((Kt_filled1[bin6] - Kt.observed[bin6])^2))
RMSE_p1.6 = sqrt((mean((Kt_filled1[bin6] - Kt.observed[bin6])^2))/(mean((Kt.observed[bin6])^2)))*100

MAE1.6 = mean(abs(Kt_filled1[bin6] - Kt.observed[bin6]))
MAE_p1.6 = (mean(abs(Kt_filled1[bin6] - Kt.observed[bin6]))/mean(Kt.observed[bin6]))*100
```

# Example 1.2: Perform imputation with KalmanRun and state space representation of arima model

``` {r}
Kt_filled2 = na_kalman(Kt, 
                        model = "auto.arima", smooth = TRUE)
```

``` {r}
# bin 1

MBE2.1 = mean(Kt_filled2[bin1] - Kt.observed[bin1])
MBE_p2.1 = (mean(Kt_filled2[bin1] - Kt.observed[bin1])/mean(Kt.observed[bin1]))*100

RMSE2.1 = sqrt(mean((Kt_filled2[bin1] - Kt.observed[bin1])^2))
RMSE_p2.1 = sqrt((mean((Kt_filled2[bin1] - Kt.observed[bin1])^2))/(mean((Kt.observed[bin1])^2)))*100

MAE2.1 = mean(abs(Kt_filled2[bin1] - Kt.observed[bin1]))
MAE_p2.1 = (mean(abs(Kt_filled2[bin1] - Kt.observed[bin1]))/mean(Kt.observed[bin1]))*100

# bin 2

MBE2.2 = mean(Kt_filled2[bin2] - Kt.observed[bin2])
MBE_p2.2 = (mean(Kt_filled2[bin2] - Kt.observed[bin2])/mean(Kt.observed[bin2]))*100

RMSE2.2 = sqrt(mean((Kt_filled2[bin2] - Kt.observed[bin2])^2))
RMSE_p2.2 = sqrt((mean((Kt_filled2[bin2] - Kt.observed[bin2])^2))/(mean((Kt.observed[bin2])^2)))*100

MAE2.2 = mean(abs(Kt_filled2[bin2] - Kt.observed[bin2]))
MAE_p2.2 = (mean(abs(Kt_filled2[bin2] - Kt.observed[bin2]))/mean(Kt.observed[bin2]))*100

# bin 3

MBE2.3 = mean(Kt_filled2[bin3] - Kt.observed[bin3])
MBE_p2.3 = (mean(Kt_filled2[bin3] - Kt.observed[bin3])/mean(Kt.observed[bin3]))*100

RMSE2.3 = sqrt(mean((Kt_filled2[bin3] - Kt.observed[bin3])^2))
RMSE_p2.3 = sqrt((mean((Kt_filled2[bin3] - Kt.observed[bin3])^2))/(mean((Kt.observed[bin3])^2)))*100

MAE2.3 = mean(abs(Kt_filled2[bin3] - Kt.observed[bin3]))
MAE_p2.3 = (mean(abs(Kt_filled2[bin3] - Kt.observed[bin3]))/mean(Kt.observed[bin3]))*100

# bin 4

MBE2.4 = mean(Kt_filled2[bin4] - Kt.observed[bin4])
MBE_p2.4 = (mean(Kt_filled2[bin4] - Kt.observed[bin4])/mean(Kt.observed[bin4]))*100

RMSE2.4 = sqrt(mean((Kt_filled2[bin4] - Kt.observed[bin4])^2))
RMSE_p2.4 = sqrt((mean((Kt_filled2[bin4] - Kt.observed[bin4])^2))/(mean((Kt.observed[bin4])^2)))*100

MAE2.4 = mean(abs(Kt_filled2[bin4] - Kt.observed[bin4]))
MAE_p2.4 = (mean(abs(Kt_filled2[bin4] - Kt.observed[bin4]))/mean(Kt.observed[bin4]))*100

# bin 5

MBE2.5 = mean(Kt_filled2[bin5] - Kt.observed[bin5])
MBE_p2.5 = (mean(Kt_filled2[bin5] - Kt.observed[bin5])/mean(Kt.observed[bin5]))*100

RMSE2.5 = sqrt(mean((Kt_filled2[bin5] - Kt.observed[bin5])^2))
RMSE_p2.5 = sqrt((mean((Kt_filled2[bin5] - Kt.observed[bin5])^2))/(mean((Kt.observed[bin5])^2)))*100

MAE2.5 = mean(abs(Kt_filled2[bin5] - Kt.observed[bin5]))
MAE_p2.5 = (mean(abs(Kt_filled2[bin5] - Kt.observed[bin5]))/mean(Kt.observed[bin5]))*100

# bin 6

MBE2.6 = mean(Kt_filled2[bin6] - Kt.observed[bin6])
MBE_p2.6 = (mean(Kt_filled2[bin6] - Kt.observed[bin6])/mean(Kt.observed[bin6]))*100

RMSE2.6 = sqrt(mean((Kt_filled2[bin6] - Kt.observed[bin6])^2))
RMSE_p2.6 = sqrt((mean((Kt_filled2[bin6] - Kt.observed[bin6])^2))/(mean((Kt.observed[bin6])^2)))*100

MAE2.6 = mean(abs(Kt_filled2[bin6] - Kt.observed[bin6]))
MAE_p2.6 = (mean(abs(Kt_filled2[bin6] - Kt.observed[bin6]))/mean(Kt.observed[bin6]))*100
```

# Example 1.3: Perform imputation with KalmanSmooth and StructTS model with additional parameters

``` {r}
Kt_filled3 = na_kalman(Kt, 
                        model = "StructTS", smooth = TRUE, 
                        type = "trend")
```

``` {r}
# bin 1

MBE3.1 = mean(Kt_filled3[bin1] - Kt.observed[bin1])
MBE_p3.1 = (mean(Kt_filled3[bin1] - Kt.observed[bin1])/mean(Kt.observed[bin1]))*100

RMSE3.1 = sqrt(mean((Kt_filled3[bin1] - Kt.observed[bin1])^2))
RMSE_p3.1 = sqrt((mean((Kt_filled3[bin1] - Kt.observed[bin1])^2))/(mean((Kt.observed[bin1])^2)))*100

MAE3.1 = mean(abs(Kt_filled3[bin1] - Kt.observed[bin1]))
MAE_p3.1 = (mean(abs(Kt_filled3[bin1] - Kt.observed[bin1]))/mean(Kt.observed[bin1]))*100

# bin 2

MBE3.2 = mean(Kt_filled3[bin2] - Kt.observed[bin2])
MBE_p3.2 = (mean(Kt_filled3[bin2] - Kt.observed[bin2])/mean(Kt.observed[bin2]))*100

RMSE3.2 = sqrt(mean((Kt_filled3[bin2] - Kt.observed[bin2])^2))
RMSE_p3.2 = sqrt((mean((Kt_filled3[bin2] - Kt.observed[bin2])^2))/(mean((Kt.observed[bin2])^2)))*100

MAE3.2 = mean(abs(Kt_filled3[bin2] - Kt.observed[bin2]))
MAE_p3.2 = (mean(abs(Kt_filled3[bin2] - Kt.observed[bin2]))/mean(Kt.observed[bin2]))*100

# bin 3

MBE3.3 = mean(Kt_filled3[bin3] - Kt.observed[bin3])
MBE_p3.3 = (mean(Kt_filled3[bin3] - Kt.observed[bin3])/mean(Kt.observed[bin3]))*100

RMSE3.3 = sqrt(mean((Kt_filled3[bin3] - Kt.observed[bin3])^2))
RMSE_p3.3 = sqrt((mean((Kt_filled3[bin3] - Kt.observed[bin3])^2))/(mean((Kt.observed[bin3])^2)))*100

MAE3.3 = mean(abs(Kt_filled3[bin3] - Kt.observed[bin3]))
MAE_p3.3 = (mean(abs(Kt_filled3[bin3] - Kt.observed[bin3]))/mean(Kt.observed[bin3]))*100

# bin 4

MBE3.4 = mean(Kt_filled3[bin4] - Kt.observed[bin4])
MBE_p3.4 = (mean(Kt_filled3[bin4] - Kt.observed[bin4])/mean(Kt.observed[bin4]))*100

RMSE3.4 = sqrt(mean((Kt_filled3[bin4] - Kt.observed[bin4])^2))
RMSE_p3.4 = sqrt((mean((Kt_filled3[bin4] - Kt.observed[bin4])^2))/(mean((Kt.observed[bin4])^2)))*100

MAE3.4 = mean(abs(Kt_filled3[bin4] - Kt.observed[bin4]))
MAE_p3.4 = (mean(abs(Kt_filled3[bin4] - Kt.observed[bin4]))/mean(Kt.observed[bin4]))*100

# bin 5

MBE3.5 = mean(Kt_filled3[bin5] - Kt.observed[bin5])
MBE_p3.5 = (mean(Kt_filled3[bin5] - Kt.observed[bin5])/mean(Kt.observed[bin5]))*100

RMSE3.5 = sqrt(mean((Kt_filled3[bin5] - Kt.observed[bin5])^2))
RMSE_p3.5 = sqrt((mean((Kt_filled3[bin5] - Kt.observed[bin5])^2))/(mean((Kt.observed[bin5])^2)))*100

MAE3.5 = mean(abs(Kt_filled3[bin5] - Kt.observed[bin5]))
MAE_p3.5 = (mean(abs(Kt_filled3[bin5] - Kt.observed[bin5]))/mean(Kt.observed[bin5]))*100

# bin 6

MBE3.6 = mean(Kt_filled3[bin6] - Kt.observed[bin6])
MBE_p3.6 = (mean(Kt_filled3[bin6] - Kt.observed[bin6])/mean(Kt.observed[bin6]))*100

RMSE3.6 = sqrt(mean((Kt_filled3[bin6] - Kt.observed[bin6])^2))
RMSE_p3.6 = sqrt((mean((Kt_filled3[bin6] - Kt.observed[bin6])^2))/(mean((Kt.observed[bin6])^2)))*100

MAE3.6 = mean(abs(Kt_filled3[bin6] - Kt.observed[bin6]))
MAE_p3.6 = (mean(abs(Kt_filled3[bin6] - Kt.observed[bin6]))/mean(Kt.observed[bin6]))*100
```

# Example 2.1: Perform linear interpolation

``` {r}

Kt_filled4 = na_interpolation(Kt, 
                        option = "linear")

#ggplot_na_imputations(x.withNA = Kt[1:100], 
 #                  x.withImputations = Kt_filled4[1:100],
  #                 x.withTruth = Kt.observed[1:100], ylab = "Kt Value") 
summary(Kt.observed)
summary(Kt_filled4)

MSPE4 = mean((Kt.observed[ind] - Kt_filled4[ind])^2)
MAPE4 = mean(abs(Kt.observed[ind] - Kt_filled4[ind]))

MSPE4*1000
MAPE4*1000
```

``` {r}
# bin 1

MBE4.1 = mean(Kt_filled4[bin1] - Kt.observed[bin1])
MBE_p4.1 = (mean(Kt_filled4[bin1] - Kt.observed[bin1])/mean(Kt.observed[bin1]))*100

RMSE4.1 = sqrt(mean((Kt_filled4[bin1] - Kt.observed[bin1])^2))
RMSE_p4.1 = sqrt((mean((Kt_filled4[bin1] - Kt.observed[bin1])^2))/(mean((Kt.observed[bin1])^2)))*100

MAE4.1 = mean(abs(Kt_filled4[bin1] - Kt.observed[bin1]))
MAE_p4.1 = (mean(abs(Kt_filled4[bin1] - Kt.observed[bin1]))/mean(Kt.observed[bin1]))*100

# bin 2

MBE4.2 = mean(Kt_filled4[bin2] - Kt.observed[bin2])
MBE_p4.2 = (mean(Kt_filled4[bin2] - Kt.observed[bin2])/mean(Kt.observed[bin2]))*100

RMSE4.2 = sqrt(mean((Kt_filled4[bin2] - Kt.observed[bin2])^2))
RMSE_p4.2 = sqrt((mean((Kt_filled4[bin2] - Kt.observed[bin2])^2))/(mean((Kt.observed[bin2])^2)))*100

MAE4.2 = mean(abs(Kt_filled4[bin2] - Kt.observed[bin2]))
MAE_p4.2 = (mean(abs(Kt_filled4[bin2] - Kt.observed[bin2]))/mean(Kt.observed[bin2]))*100

# bin 3

MBE4.3 = mean(Kt_filled4[bin3] - Kt.observed[bin3])
MBE_p4.3 = (mean(Kt_filled4[bin3] - Kt.observed[bin3])/mean(Kt.observed[bin3]))*100

RMSE4.3 = sqrt(mean((Kt_filled4[bin3] - Kt.observed[bin3])^2))
RMSE_p4.3 = sqrt((mean((Kt_filled4[bin3] - Kt.observed[bin3])^2))/(mean((Kt.observed[bin3])^2)))*100

MAE4.3 = mean(abs(Kt_filled4[bin3] - Kt.observed[bin3]))
MAE_p4.3 = (mean(abs(Kt_filled4[bin3] - Kt.observed[bin3]))/mean(Kt.observed[bin3]))*100

#bin 4

MBE4.4 = mean(Kt_filled4[bin4] - Kt.observed[bin4])
MBE_p4.4 = (mean(Kt_filled4[bin4] - Kt.observed[bin4])/mean(Kt.observed[bin4]))*100

RMSE4.4 = sqrt(mean((Kt_filled4[bin4] - Kt.observed[bin4])^2))
RMSE_p4.4 = sqrt((mean((Kt_filled4[bin4] - Kt.observed[bin4])^2))/(mean((Kt.observed[bin4])^2)))*100

MAE4.4 = mean(abs(Kt_filled4[bin4] - Kt.observed[bin4]))
MAE_p4.4 = (mean(abs(Kt_filled4[bin4] - Kt.observed[bin4]))/mean(Kt.observed[bin4]))*100

# bin 5

MBE4.5 = mean(Kt_filled4[bin5] - Kt.observed[bin5])
MBE_p4.5 = (mean(Kt_filled4[bin5] - Kt.observed[bin5])/mean(Kt.observed[bin5]))*100

RMSE4.5 = sqrt(mean((Kt_filled4[bin5] - Kt.observed[bin5])^2))
RMSE_p4.5 = sqrt((mean((Kt_filled4[bin5] - Kt.observed[bin5])^2))/(mean((Kt.observed[bin5])^2)))*100

MAE4.5 = mean(abs(Kt_filled4[bin5] - Kt.observed[bin5]))
MAE_p4.5 = (mean(abs(Kt_filled4[bin5] - Kt.observed[bin5]))/mean(Kt.observed[bin5]))*100

# bin 6

MBE4.6 = mean(Kt_filled4[bin6] - Kt.observed[bin6])
MBE_p4.6 = (mean(Kt_filled4[bin6] - Kt.observed[bin6])/mean(Kt.observed[bin6]))*100

RMSE4.6 = sqrt(mean((Kt_filled4[bin6] - Kt.observed[bin6])^2))
RMSE_p4.6 = sqrt((mean((Kt_filled4[bin6] - Kt.observed[bin6])^2))/(mean((Kt.observed[bin6])^2)))*100

MAE4.6 = mean(abs(Kt_filled4[bin6] - Kt.observed[bin6]))
MAE_p4.6 = (mean(abs(Kt_filled4[bin6] - Kt.observed[bin6]))/mean(Kt.observed[bin6]))*100
```

# Example 2.2: Perform spline interpolation

``` {r}
Kt_filled5 = na_interpolation(Kt, 
                        option = "spline")
```

``` {r}
# bin 1

MBE5.1 = mean(Kt_filled5[bin1] - Kt.observed[bin1])
MBE_p5.1 = (mean(Kt_filled5[bin1] - Kt.observed[bin1])/mean(Kt.observed[bin1]))*100

RMSE5.1 = sqrt(mean((Kt_filled5[bin1] - Kt.observed[bin1])^2))
RMSE_p5.1 = sqrt((mean((Kt_filled5[bin1] - Kt.observed[bin1])^2))/(mean((Kt.observed[bin1])^2)))*100

MAE5.1 = mean(abs(Kt_filled5[bin1] - Kt.observed[bin1]))
MAE_p5.1 = (mean(abs(Kt_filled5[bin1] - Kt.observed[bin1]))/mean(Kt.observed[bin1]))*100

# bin 2

MBE5.2 = mean(Kt_filled5[bin2] - Kt.observed[bin2])
MBE_p5.2 = (mean(Kt_filled5[bin2] - Kt.observed[bin2])/mean(Kt.observed[bin2]))*100

RMSE5.2 = sqrt(mean((Kt_filled5[bin2] - Kt.observed[bin2])^2))
RMSE_p5.2 = sqrt((mean((Kt_filled5[bin2] - Kt.observed[bin2])^2))/(mean((Kt.observed[bin2])^2)))*100

MAE5.2 = mean(abs(Kt_filled5[bin2] - Kt.observed[bin2]))
MAE_p5.2 = (mean(abs(Kt_filled5[bin2] - Kt.observed[bin2]))/mean(Kt.observed[bin2]))*100

# bin 3

MBE5.3 = mean(Kt_filled5[bin3] - Kt.observed[bin3])
MBE_p5.3 = (mean(Kt_filled5[bin3] - Kt.observed[bin3])/mean(Kt.observed[bin3]))*100

RMSE5.3 = sqrt(mean((Kt_filled5[bin3] - Kt.observed[bin3])^2))
RMSE_p5.3 = sqrt((mean((Kt_filled5[bin3] - Kt.observed[bin3])^2))/(mean((Kt.observed[bin3])^2)))*100

MAE5.3 = mean(abs(Kt_filled5[bin3] - Kt.observed[bin3]))
MAE_p5.3 = (mean(abs(Kt_filled5[bin3] - Kt.observed[bin3]))/mean(Kt.observed[bin3]))*100

#bin 4

MBE5.4 = mean(Kt_filled5[bin4] - Kt.observed[bin4])
MBE_p5.4 = (mean(Kt_filled5[bin4] - Kt.observed[bin4])/mean(Kt.observed[bin4]))*100

RMSE5.4 = sqrt(mean((Kt_filled5[bin4] - Kt.observed[bin4])^2))
RMSE_p5.4 = sqrt((mean((Kt_filled5[bin4] - Kt.observed[bin4])^2))/(mean((Kt.observed[bin4])^2)))*100

MAE5.4 = mean(abs(Kt_filled5[bin4] - Kt.observed[bin4]))
MAE_p5.4 = (mean(abs(Kt_filled5[bin4] - Kt.observed[bin4]))/mean(Kt.observed[bin4]))*100

# bin 5

MBE5.5 = mean(Kt_filled5[bin5] - Kt.observed[bin5])
MBE_p5.5 = (mean(Kt_filled5[bin5] - Kt.observed[bin5])/mean(Kt.observed[bin5]))*100

RMSE5.5 = sqrt(mean((Kt_filled5[bin5] - Kt.observed[bin5])^2))
RMSE_p5.5 = sqrt((mean((Kt_filled5[bin5] - Kt.observed[bin5])^2))/(mean((Kt.observed[bin5])^2)))*100

MAE5.5 = mean(abs(Kt_filled5[bin5] - Kt.observed[bin5]))
MAE_p5.5 = (mean(abs(Kt_filled5[bin5] - Kt.observed[bin5]))/mean(Kt.observed[bin5]))*100

# bin 6

MBE5.6 = mean(Kt_filled5[bin6] - Kt.observed[bin6])
MBE_p5.6 = (mean(Kt_filled5[bin6] - Kt.observed[bin6])/mean(Kt.observed[bin6]))*100

RMSE5.6 = sqrt(mean((Kt_filled5[bin6] - Kt.observed[bin6])^2))
RMSE_p5.6 = sqrt((mean((Kt_filled5[bin6] - Kt.observed[bin6])^2))/(mean((Kt.observed[bin6])^2)))*100

MAE5.6 = mean(abs(Kt_filled5[bin6] - Kt.observed[bin6]))
MAE_p5.6 = (mean(abs(Kt_filled5[bin6] - Kt.observed[bin6]))/mean(Kt.observed[bin6]))*100
```

# Example 2.3: Perform stine interpolation

``` {r}
Kt_filled6 = na_interpolation(Kt, 
                        option = "stine")

#plotNA.imputations(x.withNA = Kt[1:100], 
#                   x.withImputations = Kt_filled6[1:100],
#                   x.withTruth = Kt.observed[1:100], ylab = "Kt Value") 

summary(Kt.observed)
summary(Kt_filled6)

MSPE6 = mean((Kt.observed[ind] - Kt_filled6[ind])^2)
MAPE6 = mean(abs(Kt.observed[ind] - Kt_filled6[ind]))

MSPE6*1000
MAPE6*1000
```


``` {r}
# bin 1

MBE6.1 = mean(Kt_filled6[bin1] - Kt.observed[bin1])
MBE_p6.1 = (mean(Kt_filled6[bin1] - Kt.observed[bin1])/mean(Kt.observed[bin1]))*100

RMSE6.1 = sqrt(mean((Kt_filled6[bin1] - Kt.observed[bin1])^2))
RMSE_p6.1 = sqrt((mean((Kt_filled6[bin1] - Kt.observed[bin1])^2))/(mean((Kt.observed[bin1])^2)))*100

MAE6.1 = mean(abs(Kt_filled6[bin1] - Kt.observed[bin1]))
MAE_p6.1 = (mean(abs(Kt_filled6[bin1] - Kt.observed[bin1]))/mean(Kt.observed[bin1]))*100

# bin 2

MBE6.2 = mean(Kt_filled6[bin2] - Kt.observed[bin2])
MBE_p6.2 = (mean(Kt_filled6[bin2] - Kt.observed[bin2])/mean(Kt.observed[bin2]))*100

RMSE6.2 = sqrt(mean((Kt_filled6[bin2] - Kt.observed[bin2])^2))
RMSE_p6.2 = sqrt((mean((Kt_filled6[bin2] - Kt.observed[bin2])^2))/(mean((Kt.observed[bin2])^2)))*100

MAE6.2 = mean(abs(Kt_filled6[bin2] - Kt.observed[bin2]))
MAE_p6.2 = (mean(abs(Kt_filled6[bin2] - Kt.observed[bin2]))/mean(Kt.observed[bin2]))*100

# bin 3

MBE6.3 = mean(Kt_filled6[bin3] - Kt.observed[bin3])
MBE_p6.3 = (mean(Kt_filled6[bin3] - Kt.observed[bin3])/mean(Kt.observed[bin3]))*100

RMSE6.3 = sqrt(mean((Kt_filled6[bin3] - Kt.observed[bin3])^2))
RMSE_p6.3 = sqrt((mean((Kt_filled6[bin3] - Kt.observed[bin3])^2))/(mean((Kt.observed[bin3])^2)))*100

MAE6.3 = mean(abs(Kt_filled6[bin3] - Kt.observed[bin3]))
MAE_p6.3 = (mean(abs(Kt_filled6[bin3] - Kt.observed[bin3]))/mean(Kt.observed[bin3]))*100

# bin 4

MBE6.4 = mean(Kt_filled6[bin4] - Kt.observed[bin4])
MBE_p6.4 = (mean(Kt_filled6[bin4] - Kt.observed[bin4])/mean(Kt.observed[bin4]))*100

RMSE6.4 = sqrt(mean((Kt_filled6[bin4] - Kt.observed[bin4])^2))
RMSE_p6.4 = sqrt((mean((Kt_filled6[bin4] - Kt.observed[bin4])^2))/(mean((Kt.observed[bin4])^2)))*100

MAE6.4 = mean(abs(Kt_filled6[bin4] - Kt.observed[bin4]))
MAE_p6.4 = (mean(abs(Kt_filled6[bin4] - Kt.observed[bin4]))/mean(Kt.observed[bin4]))*100

# bin 5

MBE6.5 = mean(Kt_filled6[bin5] - Kt.observed[bin5])
MBE_p6.5 = (mean(Kt_filled6[bin5] - Kt.observed[bin5])/mean(Kt.observed[bin5]))*100

RMSE6.5 = sqrt(mean((Kt_filled6[bin5] - Kt.observed[bin5])^2))
RMSE_p6.5 = sqrt((mean((Kt_filled6[bin5] - Kt.observed[bin5])^2))/(mean((Kt.observed[bin5])^2)))*100

MAE6.5 = mean(abs(Kt_filled6[bin5] - Kt.observed[bin5]))
MAE_p6.5 = (mean(abs(Kt_filled6[bin5] - Kt.observed[bin5]))/mean(Kt.observed[bin5]))*100

# bin 6

MBE6.6 = mean(Kt_filled6[bin6] - Kt.observed[bin6])
MBE_p6.6 = (mean(Kt_filled6[bin6] - Kt.observed[bin6])/mean(Kt.observed[bin6]))*100

RMSE6.6 = sqrt(mean((Kt_filled6[bin6] - Kt.observed[bin6])^2))
RMSE_p6.6 = sqrt((mean((Kt_filled6[bin6] - Kt.observed[bin6])^2))/(mean((Kt.observed[bin6])^2)))*100

MAE6.6 = mean(abs(Kt_filled6[bin6] - Kt.observed[bin6]))
MAE_p6.6 = (mean(abs(Kt_filled6[bin6] - Kt.observed[bin6]))/mean(Kt.observed[bin6]))*100
```


# Example 4.1: Perform imputation with simple moving average

``` {r}
# default

Kt_filled9 = na_ma(Kt, weighting = "simple")
```

``` {r}
# bin 1

MBE9.1 = mean(Kt_filled9[bin1] - Kt.observed[bin1])
MBE_p9.1 = (mean(Kt_filled9[bin1] - Kt.observed[bin1])/mean(Kt.observed[bin1]))*100

RMSE9.1 = sqrt(mean((Kt_filled9[bin1] - Kt.observed[bin1])^2))
RMSE_p9.1 = sqrt((mean((Kt_filled9[bin1] - Kt.observed[bin1])^2))/(mean((Kt.observed[bin1])^2)))*100

MAE9.1 = mean(abs(Kt_filled9[bin1] - Kt.observed[bin1]))
MAE_p9.1 = (mean(abs(Kt_filled9[bin1] - Kt.observed[bin1]))/mean(Kt.observed[bin1]))*100

# bin 2

MBE9.2 = mean(Kt_filled9[bin2] - Kt.observed[bin2])
MBE_p9.2 = (mean(Kt_filled9[bin2] - Kt.observed[bin2])/mean(Kt.observed[bin2]))*100

RMSE9.2 = sqrt(mean((Kt_filled9[bin2] - Kt.observed[bin2])^2))
RMSE_p9.2 = sqrt((mean((Kt_filled9[bin2] - Kt.observed[bin2])^2))/(mean((Kt.observed[bin2])^2)))*100

MAE9.2 = mean(abs(Kt_filled9[bin2] - Kt.observed[bin2]))
MAE_p9.2 = (mean(abs(Kt_filled9[bin2] - Kt.observed[bin2]))/mean(Kt.observed[bin2]))*100

# bin 3

MBE9.3 = mean(Kt_filled9[bin3] - Kt.observed[bin3])
MBE_p9.3 = (mean(Kt_filled9[bin3] - Kt.observed[bin3])/mean(Kt.observed[bin3]))*100

RMSE9.3 = sqrt(mean((Kt_filled9[bin3] - Kt.observed[bin3])^2))
RMSE_p9.3 = sqrt((mean((Kt_filled9[bin3] - Kt.observed[bin3])^2))/(mean((Kt.observed[bin3])^2)))*100

MAE9.3 = mean(abs(Kt_filled9[bin3] - Kt.observed[bin3]))
MAE_p9.3 = (mean(abs(Kt_filled9[bin3] - Kt.observed[bin3]))/mean(Kt.observed[bin3]))*100

# bin 4

MBE9.4 = mean(Kt_filled9[bin4] - Kt.observed[bin4])
MBE_p9.4 = (mean(Kt_filled9[bin4] - Kt.observed[bin4])/mean(Kt.observed[bin4]))*100

RMSE9.4 = sqrt(mean((Kt_filled9[bin4] - Kt.observed[bin4])^2))
RMSE_p9.4 = sqrt((mean((Kt_filled9[bin4] - Kt.observed[bin4])^2))/(mean((Kt.observed[bin4])^2)))*100

MAE9.4 = mean(abs(Kt_filled9[bin4] - Kt.observed[bin4]))
MAE_p9.4 = (mean(abs(Kt_filled9[bin4] - Kt.observed[bin4]))/mean(Kt.observed[bin4]))*100

# bin 5

MBE9.5 = mean(Kt_filled9[bin5] - Kt.observed[bin5])
MBE_p9.5 = (mean(Kt_filled9[bin5] - Kt.observed[bin5])/mean(Kt.observed[bin5]))*100

RMSE9.5 = sqrt(mean((Kt_filled9[bin5] - Kt.observed[bin5])^2))
RMSE_p9.5 = sqrt((mean((Kt_filled9[bin5] - Kt.observed[bin5])^2))/(mean((Kt.observed[bin5])^2)))*100

MAE9.5 = mean(abs(Kt_filled9[bin5] - Kt.observed[bin5]))
MAE_p9.5 = (mean(abs(Kt_filled9[bin5] - Kt.observed[bin5]))/mean(Kt.observed[bin5]))*100

# bin 6

MBE9.6 = mean(Kt_filled9[bin6] - Kt.observed[bin6])
MBE_p9.6 = (mean(Kt_filled9[bin6] - Kt.observed[bin6])/mean(Kt.observed[bin6]))*100

RMSE9.6 = sqrt(mean((Kt_filled9[bin6] - Kt.observed[bin6])^2))
RMSE_p9.6 = sqrt((mean((Kt_filled9[bin6] - Kt.observed[bin6])^2))/(mean((Kt.observed[bin6])^2)))*100

MAE9.6 = mean(abs(Kt_filled9[bin6] - Kt.observed[bin6]))
MAE_p9.6 = (mean(abs(Kt_filled9[bin6] - Kt.observed[bin6]))/mean(Kt.observed[bin6]))*100
```

# Example 4.2: Perform imputation with linear weighted moving average

``` {r}
# default

Kt_filled10 = na_ma(Kt, weighting = "linear")
```


``` {r}
# bin 1

MBE10.1 = mean(Kt_filled10[bin1] - Kt.observed[bin1])
MBE_p10.1 = (mean(Kt_filled10[bin1] - Kt.observed[bin1])/mean(Kt.observed[bin1]))*100

RMSE10.1 = sqrt(mean((Kt_filled10[bin1] - Kt.observed[bin1])^2))
RMSE_p10.1 = sqrt((mean((Kt_filled10[bin1] - Kt.observed[bin1])^2))/(mean((Kt.observed[bin1])^2)))*100

MAE10.1 = mean(abs(Kt_filled10[bin1] - Kt.observed[bin1]))
MAE_p10.1 = (mean(abs(Kt_filled10[bin1] - Kt.observed[bin1]))/mean(Kt.observed[bin1]))*100

# bin 2

MBE10.2 = mean(Kt_filled10[bin2] - Kt.observed[bin2])
MBE_p10.2 = (mean(Kt_filled10[bin2] - Kt.observed[bin2])/mean(Kt.observed[bin2]))*100

RMSE10.2 = sqrt(mean((Kt_filled10[bin2] - Kt.observed[bin2])^2))
RMSE_p10.2 = sqrt((mean((Kt_filled10[bin2] - Kt.observed[bin2])^2))/(mean((Kt.observed[bin2])^2)))*100

MAE10.2 = mean(abs(Kt_filled10[bin2] - Kt.observed[bin2]))
MAE_p10.2 = (mean(abs(Kt_filled10[bin2] - Kt.observed[bin2]))/mean(Kt.observed[bin2]))*100

# bin 3

MBE10.3 = mean(Kt_filled10[bin3] - Kt.observed[bin3])
MBE_p10.3 = (mean(Kt_filled10[bin3] - Kt.observed[bin3])/mean(Kt.observed[bin3]))*100

RMSE10.3 = sqrt(mean((Kt_filled10[bin3] - Kt.observed[bin3])^2))
RMSE_p10.3 = sqrt((mean((Kt_filled10[bin3] - Kt.observed[bin3])^2))/(mean((Kt.observed[bin3])^2)))*100

MAE10.3 = mean(abs(Kt_filled10[bin3] - Kt.observed[bin3]))
MAE_p10.3 = (mean(abs(Kt_filled10[bin3] - Kt.observed[bin3]))/mean(Kt.observed[bin3]))*100

# bin 4

MBE10.4 = mean(Kt_filled10[bin4] - Kt.observed[bin4])
MBE_p10.4 = (mean(Kt_filled10[bin4] - Kt.observed[bin4])/mean(Kt.observed[bin4]))*100

RMSE10.4 = sqrt(mean((Kt_filled10[bin4] - Kt.observed[bin4])^2))
RMSE_p10.4 = sqrt((mean((Kt_filled10[bin4] - Kt.observed[bin4])^2))/(mean((Kt.observed[bin4])^2)))*100

MAE10.4 = mean(abs(Kt_filled10[bin4] - Kt.observed[bin4]))
MAE_p10.4 = (mean(abs(Kt_filled10[bin4] - Kt.observed[bin4]))/mean(Kt.observed[bin4]))*100

# bin 5

MBE10.5 = mean(Kt_filled10[bin5] - Kt.observed[bin5])
MBE_p10.5 = (mean(Kt_filled10[bin5] - Kt.observed[bin5])/mean(Kt.observed[bin5]))*100

RMSE10.5 = sqrt(mean((Kt_filled10[bin5] - Kt.observed[bin5])^2))
RMSE_p10.5 = sqrt((mean((Kt_filled10[bin5] - Kt.observed[bin5])^2))/(mean((Kt.observed[bin5])^2)))*100

MAE10.5 = mean(abs(Kt_filled10[bin5] - Kt.observed[bin5]))
MAE_p10.5 = (mean(abs(Kt_filled10[bin5] - Kt.observed[bin5]))/mean(Kt.observed[bin5]))*100

# bin 6

MBE10.6 = mean(Kt_filled10[bin6] - Kt.observed[bin6])
MBE_p10.6 = (mean(Kt_filled10[bin6] - Kt.observed[bin6])/mean(Kt.observed[bin6]))*100

RMSE10.6 = sqrt(mean((Kt_filled10[bin6] - Kt.observed[bin6])^2))
RMSE_p10.6 = sqrt((mean((Kt_filled10[bin6] - Kt.observed[bin6])^2))/(mean((Kt.observed[bin6])^2)))*100

MAE10.6 = mean(abs(Kt_filled10[bin6] - Kt.observed[bin6]))
MAE_p10.6 = (mean(abs(Kt_filled10[bin6] - Kt.observed[bin6]))/mean(Kt.observed[bin6]))*100
```

# Example 4.3: Perform imputation with exponential weighted moving average

``` {r}
# default

Kt_filled11 = na_ma(Kt, weighting = "exponential")
```

``` {r}
# bin 1

MBE11.1 = mean(Kt_filled11[bin1] - Kt.observed[bin1])
MBE_p11.1 = (mean(Kt_filled11[bin1] - Kt.observed[bin1])/mean(Kt.observed[bin1]))*100

RMSE11.1 = sqrt(mean((Kt_filled11[bin1] - Kt.observed[bin1])^2))
RMSE_p11.1 = sqrt((mean((Kt_filled11[bin1] - Kt.observed[bin1])^2))/(mean((Kt.observed[bin1])^2)))*100

MAE11.1 = mean(abs(Kt_filled11[bin1] - Kt.observed[bin1]))
MAE_p11.1 = (mean(abs(Kt_filled11[bin1] - Kt.observed[bin1]))/mean(Kt.observed[bin1]))*100

# bin 2

MBE11.2 = mean(Kt_filled11[bin2] - Kt.observed[bin2])
MBE_p11.2 = (mean(Kt_filled11[bin2] - Kt.observed[bin2])/mean(Kt.observed[bin2]))*100

RMSE11.2 = sqrt(mean((Kt_filled11[bin2] - Kt.observed[bin2])^2))
RMSE_p11.2 = sqrt((mean((Kt_filled11[bin2] - Kt.observed[bin2])^2))/(mean((Kt.observed[bin2])^2)))*100

MAE11.2 = mean(abs(Kt_filled11[bin2] - Kt.observed[bin2]))
MAE_p11.2 = (mean(abs(Kt_filled11[bin2] - Kt.observed[bin2]))/mean(Kt.observed[bin2]))*100

# bin 3

MBE11.3 = mean(Kt_filled11[bin3] - Kt.observed[bin3])
MBE_p11.3 = (mean(Kt_filled11[bin3] - Kt.observed[bin3])/mean(Kt.observed[bin3]))*100

RMSE11.3 = sqrt(mean((Kt_filled11[bin3] - Kt.observed[bin3])^2))
RMSE_p11.3 = sqrt((mean((Kt_filled11[bin3] - Kt.observed[bin3])^2))/(mean((Kt.observed[bin3])^2)))*100

MAE11.3 = mean(abs(Kt_filled11[bin3] - Kt.observed[bin3]))
MAE_p11.3 = (mean(abs(Kt_filled11[bin3] - Kt.observed[bin3]))/mean(Kt.observed[bin3]))*100

# bin 4

MBE11.4 = mean(Kt_filled11[bin4] - Kt.observed[bin4])
MBE_p11.4 = (mean(Kt_filled11[bin4] - Kt.observed[bin4])/mean(Kt.observed[bin4]))*100

RMSE11.4 = sqrt(mean((Kt_filled11[bin4] - Kt.observed[bin4])^2))
RMSE_p11.4 = sqrt((mean((Kt_filled11[bin4] - Kt.observed[bin4])^2))/(mean((Kt.observed[bin4])^2)))*100

MAE11.4 = mean(abs(Kt_filled11[bin4] - Kt.observed[bin4]))
MAE_p11.4 = (mean(abs(Kt_filled11[bin4] - Kt.observed[bin4]))/mean(Kt.observed[bin4]))*100

# bin 5

MBE11.5 = mean(Kt_filled11[bin5] - Kt.observed[bin5])
MBE_p11.5 = (mean(Kt_filled11[bin5] - Kt.observed[bin5])/mean(Kt.observed[bin5]))*100

RMSE11.5 = sqrt(mean((Kt_filled11[bin5] - Kt.observed[bin5])^2))
RMSE_p11.5 = sqrt((mean((Kt_filled11[bin5] - Kt.observed[bin5])^2))/(mean((Kt.observed[bin5])^2)))*100

MAE11.5 = mean(abs(Kt_filled11[bin5] - Kt.observed[bin5]))
MAE_p11.5 = (mean(abs(Kt_filled11[bin5] - Kt.observed[bin5]))/mean(Kt.observed[bin5]))*100

# bin 6

MBE11.6 = mean(Kt_filled11[bin6] - Kt.observed[bin6])
MBE_p11.6 = (mean(Kt_filled11[bin6] - Kt.observed[bin6])/mean(Kt.observed[bin6]))*100

RMSE11.6 = sqrt(mean((Kt_filled11[bin6] - Kt.observed[bin6])^2))
RMSE_p11.6 = sqrt((mean((Kt_filled11[bin6] - Kt.observed[bin6])^2))/(mean((Kt.observed[bin6])^2)))*100

MAE11.6 = mean(abs(Kt_filled11[bin6] - Kt.observed[bin6]))
MAE_p11.6 = (mean(abs(Kt_filled11[bin6] - Kt.observed[bin6]))/mean(Kt.observed[bin6]))*100
```

``` {r}
RMSE = cbind(rbind(round(RMSE4.1*1000, 1), round(RMSE4.2*1000, 1), round(RMSE4.3*1000, 1), round(RMSE4.4*1000, 1), round(RMSE4.5*1000, 1), round(RMSE4.6*1000, 1)), 
             rbind(round(RMSE6.1*1000, 1), round(RMSE6.2*1000, 1), round(RMSE6.3*1000, 1), round(RMSE6.4*1000, 1), round(RMSE6.5*1000, 1), round(RMSE6.6*1000, 1)),
             rbind(round(RMSE1.1*1000, 1), round(RMSE1.2*1000, 1), round(RMSE1.3*1000, 1), round(RMSE1.4*1000, 1), round(RMSE1.5*1000, 1), round(RMSE1.6*1000, 1)),
             rbind(round(RMSE2.1*1000, 1), round(RMSE2.2*1000, 1), round(RMSE2.3*1000, 1), round(RMSE2.4*1000, 1), round(RMSE2.5*1000, 1), round(RMSE2.6*1000, 1)),
             rbind(round(RMSE5.1*1000, 1), round(RMSE5.2*1000, 1), round(RMSE5.3*1000, 1), round(RMSE5.4*1000, 1), round(RMSE5.5*1000, 1), round(RMSE5.6*1000, 1)),
             rbind(round(RMSE9.1*1000, 1), round(RMSE9.2*1000, 1), round(RMSE9.3*1000, 1), round(RMSE9.4*1000, 1), round(RMSE9.5*1000, 1), round(RMSE9.6*1000, 1)),
             rbind(round(RMSE10.1*1000, 1), round(RMSE10.2*1000, 1), round(RMSE10.3*1000, 1), round(RMSE10.4*1000, 1), round(RMSE10.5*1000, 1), round(RMSE10.6*1000, 1)),
             rbind(round(RMSE11.1*1000, 1), round(RMSE11.2*1000, 1), round(RMSE11.3*1000, 1), round(RMSE11.4*1000, 1), round(RMSE11.5*1000, 1), round(RMSE11.6*1000, 1)))



RMSE_p = cbind(rbind(round(RMSE_p4.1*1000, 1), round(RMSE_p4.2*1000, 1), round(RMSE_p4.3*1000, 1), round(RMSE_p4.4*1000, 1), round(RMSE_p4.5*1000, 1), round(RMSE_p4.6*1000, 1)), 
             rbind(round(RMSE_p6.1*1000, 1), round(RMSE_p6.2*1000, 1), round(RMSE_p6.3*1000, 1), round(RMSE_p6.4*1000, 1), round(RMSE_p6.5*1000, 1), round(RMSE_p6.6*1000, 1)),
             rbind(round(RMSE_p1.1*1000, 1), round(RMSE_p1.2*1000, 1), round(RMSE_p1.3*1000, 1), round(RMSE_p1.4*1000, 1), round(RMSE_p1.5*1000, 1), round(RMSE_p1.6*1000, 1)),
             rbind(round(RMSE_p2.1*1000, 1), round(RMSE_p2.2*1000, 1), round(RMSE_p2.3*1000, 1), round(RMSE_p2.4*1000, 1), round(RMSE_p2.5*1000, 1), round(RMSE_p2.6*1000, 1)),
             rbind(round(RMSE_p5.1*1000, 1), round(RMSE_p5.2*1000, 1), round(RMSE_p5.3*1000, 1), round(RMSE_p5.4*1000, 1), round(RMSE_p5.5*1000, 1), round(RMSE_p5.6*1000, 1)),
             rbind(round(RMSE_p9.1*1000, 1), round(RMSE_p9.2*1000, 1), round(RMSE_p9.3*1000, 1), round(RMSE_p9.4*1000, 1), round(RMSE_p9.5*1000, 1), round(RMSE_p9.6*1000, 1)),
             rbind(round(RMSE_p10.1*1000, 1), round(RMSE_p10.2*1000, 1), round(RMSE_p10.3*1000, 1), round(RMSE_p10.4*1000, 1), round(RMSE_p10.5*1000, 1), round(RMSE_p10.6*1000, 1)),
             rbind(round(RMSE_p11.1*1000, 1), round(RMSE_p11.2*1000, 1), round(RMSE_p11.3*1000, 1), round(RMSE_p11.4*1000, 1), round(RMSE_p11.5*1000, 1), round(RMSE_p11.6*1000, 1)))




MAE = cbind(rbind(round(MAE4.1*1000, 1), round(MAE4.2*1000, 1), round(MAE4.3*1000, 1), round(MAE4.4*1000, 1), round(MAE4.5*1000, 1), round(MAE4.6*1000, 1)), 
             rbind(round(MAE6.1*1000, 1), round(MAE6.2*1000, 1), round(MAE6.3*1000, 1), round(MAE6.4*1000, 1), round(MAE6.5*1000, 1), round(MAE6.6*1000, 1)),
             rbind(round(MAE1.1*1000, 1), round(MAE1.2*1000, 1), round(MAE1.3*1000, 1), round(MAE1.4*1000, 1), round(MAE1.5*1000, 1), round(MAE1.6*1000, 1)),
             rbind(round(MAE2.1*1000, 1), round(MAE2.2*1000, 1), round(MAE2.3*1000, 1), round(MAE2.4*1000, 1), round(MAE2.5*1000, 1), round(MAE2.6*1000, 1)),
             rbind(round(MAE5.1*1000, 1), round(MAE5.2*1000, 1), round(MAE5.3*1000, 1), round(MAE5.4*1000, 1), round(MAE5.5*1000, 1), round(MAE5.6*1000, 1)),
             rbind(round(MAE9.1*1000, 1), round(MAE9.2*1000, 1), round(MAE9.3*1000, 1), round(MAE9.4*1000, 1), round(MAE9.5*1000, 1), round(MAE9.6*1000, 1)),
             rbind(round(MAE10.1*1000, 1), round(MAE10.2*1000, 1), round(MAE10.3*1000, 1), round(MAE10.4*1000, 1), round(MAE10.5*1000, 1), round(MAE10.6*1000, 1)),
             rbind(round(MAE11.1*1000, 1), round(MAE11.2*1000, 1), round(MAE11.3*1000, 1), round(MAE11.4*1000, 1), round(MAE11.5*1000, 1), round(MAE11.6*1000, 1)))
            




MAE_p = cbind(rbind(round(MAE_p4.1*1000, 1), round(MAE_p4.2*1000, 1), round(MAE_p4.3*1000, 1), round(MAE_p4.4*1000, 1), round(MAE_p4.5*1000, 1), round(MAE_p4.6*1000, 1)), 
             rbind(round(MAE_p6.1*1000, 1), round(MAE_p6.2*1000, 1), round(MAE_p6.3*1000, 1), round(MAE_p6.4*1000, 1), round(MAE_p6.5*1000, 1), round(MAE_p6.6*1000, 1)),
             rbind(round(MAE_p1.1*1000, 1), round(MAE_p1.2*1000, 1), round(MAE_p1.3*1000, 1), round(MAE_p1.4*1000, 1), round(MAE_p1.5*1000, 1), round(MAE_p1.6*1000, 1)),
             rbind(round(MAE_p2.1*1000, 1), round(MAE_p2.2*1000, 1), round(MAE_p2.3*1000, 1), round(MAE_p2.4*1000, 1), round(MAE_p2.5*1000, 1), round(MAE_p2.6*1000, 1)),
             rbind(round(MAE_p5.1*1000, 1), round(MAE_p5.2*1000, 1), round(MAE_p5.3*1000, 1), round(MAE_p5.4*1000, 1), round(MAE_p5.5*1000, 1), round(MAE_p5.6*1000, 1)),
             rbind(round(MAE_p9.1*1000, 1), round(MAE_p9.2*1000, 1), round(MAE_p9.3*1000, 1), round(MAE_p9.4*1000, 1), round(MAE_p9.5*1000, 1), round(MAE_p9.6*1000, 1)),
             rbind(round(MAE_p10.1*1000, 1), round(MAE_p10.2*1000, 1), round(MAE_p10.3*1000, 1), round(MAE_p10.4*1000, 1), round(MAE_p10.5*1000, 1), round(MAE_p10.6*1000, 1)),
             rbind(round(MAE_p11.1*1000, 1), round(MAE_p11.2*1000, 1), round(MAE_p11.3*1000, 1), round(MAE_p11.4*1000, 1), round(MAE_p11.5*1000, 1), round(MAE_p11.6*1000, 1)))



MBE = cbind(rbind(round(MBE4.1*1000, 1), round(MBE4.2*1000, 1), round(MBE4.3*1000, 1), round(MBE4.4*1000, 1), round(MBE4.5*1000, 1), round(MBE4.6*1000, 1)), 
             rbind(round(MBE6.1*1000, 1), round(MBE6.2*1000, 1), round(MBE6.3*1000, 1), round(MBE6.4*1000, 1), round(MBE6.5*1000, 1), round(MBE6.6*1000, 1)),
             rbind(round(MBE1.1*1000, 1), round(MBE1.2*1000, 1), round(MBE1.3*1000, 1), round(MBE1.4*1000, 1), round(MBE1.5*1000, 1), round(MBE1.6*1000, 1)),
             rbind(round(MBE2.1*1000, 1), round(MBE2.2*1000, 1), round(MBE2.3*1000, 1), round(MBE2.4*1000, 1), round(MBE2.5*1000, 1), round(MBE2.6*1000, 1)),
             rbind(round(MBE5.1*1000, 1), round(MBE5.2*1000, 1), round(MBE5.3*1000, 1), round(MBE5.4*1000, 1), round(MBE5.5*1000, 1), round(MBE5.6*1000, 1)),
             rbind(round(MBE9.1*1000, 1), round(MBE9.2*1000, 1), round(MBE9.3*1000, 1), round(MBE9.4*1000, 1), round(MBE9.5*1000, 1), round(MBE9.6*1000, 1)),
             rbind(round(MBE10.1*1000, 1), round(MBE10.2*1000, 1), round(MBE10.3*1000, 1), round(MBE10.4*1000, 1), round(MBE10.5*1000, 1), round(MBE10.6*1000, 1)),
             rbind(round(MBE11.1*1000, 1), round(MBE11.2*1000, 1), round(MBE11.3*1000, 1), round(MBE11.4*1000, 1), round(MBE11.5*1000, 1), round(MBE11.6*1000, 1)))




MBE_p = cbind(rbind(round(MBE_p4.1*1000, 1), round(MBE_p4.2*1000, 1), round(MBE_p4.3*1000, 1), round(MBE_p4.4*1000, 1), round(MBE_p4.5*1000, 1), round(MBE_p4.6*1000, 1)), 
             rbind(round(MBE_p6.1*1000, 1), round(MBE_p6.2*1000, 1), round(MBE_p6.3*1000, 1), round(MBE_p6.4*1000, 1), round(MBE_p6.5*1000, 1), round(MBE_p6.6*1000, 1)),
             rbind(round(MBE_p1.1*1000, 1), round(MBE_p1.2*1000, 1), round(MBE_p1.3*1000, 1), round(MBE_p1.4*1000, 1), round(MBE_p1.5*1000, 1), round(MBE_p1.6*1000, 1)),
             rbind(round(MBE_p2.1*1000, 1), round(MBE_p2.2*1000, 1), round(MBE_p2.3*1000, 1), round(MBE_p2.4*1000, 1), round(MBE_p2.5*1000, 1), round(MBE_p2.6*1000, 1)),
             rbind(round(MBE_p5.1*1000, 1), round(MBE_p5.2*1000, 1), round(MBE_p5.3*1000, 1), round(MBE_p5.4*1000, 1), round(MBE_p5.5*1000, 1), round(MBE_p5.6*1000, 1)),
             rbind(round(MBE_p9.1*1000, 1), round(MBE_p9.2*1000, 1), round(MBE_p9.3*1000, 1), round(MBE_p9.4*1000, 1), round(MBE_p9.5*1000, 1), round(MBE_p9.6*1000, 1)),
             rbind(round(MBE_p10.1*1000, 1), round(MBE_p10.2*1000, 1), round(MBE_p10.3*1000, 1), round(MBE_p10.4*1000, 1), round(MBE_p10.5*1000, 1), round(MBE_p10.6*1000, 1)),
             rbind(round(MBE_p11.1*1000, 1), round(MBE_p11.2*1000, 1), round(MBE_p11.3*1000, 1), round(MBE_p11.4*1000, 1), round(MBE_p11.5*1000, 1), round(MBE_p11.6*1000, 1)))


RMSE
RMSE_p
MAE
MAE_p
MBE
MBE_p
```
